\chapter{Roles, Final}

\emph{Sunday, April 19th, 6:34pm.}
Daphne Greengrass walked quietly toward the Greengrass room below theSlytherin dungeons, the privilege of an Ancient House; on her way todrop off her trunk from the Hogwarts Express, before she joined theother students for dinner. The whole private area had been hers aloneever since Malfoy had gone. Her hand, held behind her, made repeatedcome-along gestures at her huge emerald-studded trunk, which seemedhesitant to follow. Maybe the enchantments on the sturdy old familydevice needed to be reapplied; or maybe her trunk was reluctant tofollow her into Hogwarts, which was no longer safe.
There'd been a long talk between Mother and Father, after they'd beentold about Hermione; with Daphne hiding around a doorway to listen,choking back her tears and trying not to make sounds.
Mother had said that the sad fact was that if only one student diedevery year, well, that still made Hogwarts safer than Beauxbatons, letalone Durmstrang. There were more ways for a young witch to die thanbeing murdered. Beauxbatons's Transfiguration Master just wasn't on thesame level as McGonagall, Mother had said.
Father had soberly remarked how important it was for the Greengrass heirto stay at Hogwarts where all the other Noble families sent theirchildren to school (it was the reason for the old tradition of the Noblefamilies synchronizing the birth of their heirs, to put them in the sameyear of Hogwarts, if they could). And Father had said that being heiressto a Most Ancient House meant you couldn't always stay away fromtrouble.
She could have done without hearing that last part.
Daphne gulped hard, as she turned the doorknob, and opened the door.

``Miss Greengrass -'' whispered a shadowy, silvery-robed figure.
Daphne screamed and slammed the door and drew her wand and turned torun.

``Wait!'' cried the voice, now higher and louder.
Daphne paused. That couldn't \emph{possibly} be who it had sounded like.
Slowly, Daphne turned, and opened the door again.

\emph{``You!''} Daphne said in astonishment, as she saw the face beneaththe hood. ``I thought you were -''

``I come back to you now,'' the silvery-robed figure said in a strongvoice, ``at the turn of the -''

" \emph{What are you doing in my bedroom?} " shrieked Daphne.

``I heard you can cast the mist form of the Patronus Charm. Can I see?''
Daphne stared, and then her blood began to burn. ``Why?'' she said,keeping her wand level. ``So you can \emph{kill} everyone in Slytherinwho casts un-Slytherin spells? We all \emph{know} who it was hadHermione killed!''
The figure's voice rose. ``I testified under Veritaserum that I tried tohelp Miss Granger! I really was trying to help her, when I grabbed herhand on the roof, when I helped her off the floor -''
Daphne kept her wand level. ``Like your father couldn't tamper with theAurors' record, if he wanted to! I wasn't born yesterday, Mister
\emph{Malfoy!}''
Slowly, as if not to cause alarm, the silver-robed figure drew a wandfrom his robes. Daphne's hand tightened on her own wand, but then sherecognized the position of the fingers on the wand, the stance thefigure was assuming, and she drew a shocked breath -

*``Expecto Patronum!*''
Silver light leapt from the end of the other's wand - and condensed,forming a shining serpent that seemed to coil in the air as thoughnesting there.
She just gaped.

``I \emph{did} try to help Hermione Granger,'' Draco Malfoy said with alevel voice. ``Because I know the sickness at the heart of Slytherin'sHouse, the reason why so many of us can't cast the Patronus Charm anymore, is hate. Hate of Muggleborns, or just anyone really. People thinkthat's all Slytherin is about now, not cunning or ambition or honorablenobility. And I even know, because it's obvious if you just look, thatHermione Granger wasn't weak at magic.''
Daphne's mind had gone completely blank. Her eyes darted aroundnervously, just to check that there wasn't blood coming from under thedoors, like the last time Something had Broken.

``And I've also figured out,'' Draco Malfoy said quietly, as the silversnake went on shining with unmistakeable light and warmth, ``thatHermione Granger never really tried to kill me. Maybe she wasFalse-Memory-Charmed, maybe she was Legilimized, but now that she's beenmurdered, it's obvious that Miss Granger was the target in the firstplace, when somebody tried to set her up for murdering me -''

``D-do-do you know what you're \emph{saying?}'' Daphne's voice broke. IfLucius Malfoy heard his heir saying that - he'd \emph{skin} Draco andturn him into \emph{trousers!}
Draco Malfoy smiled, metallic robes gleaming in the light of his fullcorporeal Patronus; it was a smile both arrogant and dangerous, likebeing turned into a pair of leather pants was beneath his concerns.
``Yes,'' said Draco, ``but it doesn't matter now. House Malfoy isreturning House Potter's money and cancelling the debt.''
Daphne walked over to her bed and then fell on it, hoping she could wakeup from the dream once she was in bed.

``I'd like you to join a conspiracy,'' said the figure in the shiningrobes. ``Everyone in Slytherin who can cast the Patronus Charm, andeveryone who can learn. That's how we'll know to trust each other, whenthe Silvery Slytherins meet.'' With a dramatic gesture, Draco Malfoycast back his hood. ``But it won't work without \emph{you,} DaphneGreengrass. You and your family. Your mother will negotiate it withFather, but I'd like the Greengrasses to hear the proposal from you,first.'' Draco Malfoy's voice lowered grimly. ``There is much we mustspeak of, before we eat dinner.''

\begin{center}\rule{3in}{0.4pt}\end{center}
Harry Potter had, apparently, taken to being invisible; they'd glimpsedhis hand only briefly, when he was handing them the list, written onstrange not-parchment. Harry had explained that, all things considered,he didn't really think it was smart for him to be \emph{findable} excepton special occasions, so he was just going to deal with people as adisembodied floating voice from now on, or as a brilliant silver lightthat hid behind corners where nobody could see it, and which couldalways find his friends no matter where they tried to hide. It was, inall honesty, one of the creepiest things which Fred and George had everheard, over a lifetime which had included filling the shoes of everystudent in second-year Slytherin with Transfigured live millipedes. Fredand George didn't think this could possibly be good for anyone's sanity,but they didn't know what to say. It couldn't be denied, they'd seenwith their own four eyes, that Hogwarts\ldots{}

\ldots{}wasn't safe\ldots{}

``I don't know who you went to for the False Memory Charm on RitaSkeeter,'' said the sourceless voice of Harry Potter. ``Whoever itis\ldots{} probably \emph{won't} be able to fill this order directly,but they may know someone who can get things from the Muggle world. And
- I know it may cost extra, but as few people as possible should knowthat Harry Potter is related to this.'' Another flash of a small boy'shand, and a bag hit the ground with the clinking noise. ``Some of theseitems are expensive even in the Muggle world, and your contact may haveto go outside Britain; but one hundred Galleons will be enough to payfor it all, I hope. I'd tell you where the Galleons came from, but Idon't want to spoil tomorrow's surprise.''

``What \emph{is} this stuff?'' said Fred or George, as they looked overthe list. ``Our father is a Muggle expert -''

``- and we don't recognize \emph{half} this stuff -''

``- why, we don't recognize any of it -''

``- just what are you planning to \emph{do?}''

``Things have become serious,'' Harry's voice said softly. ``I don'tknow what I'll have to do. I may need the power of the Muggles, not justthe wizards, before this is done - and I might need it right away, withno time to prepare. I'm not \emph{planning} to use any of this. I justwant it around in case of\ldots{} contingencies.'' Harry's voice paused.
``Obviously I owe you more than I can ever repay and you won't
\emph{let} me give you \emph{any} of what you deserve, I don't even knowhow to say thank you properly, and all I can do is hope that somedaywhen you grow up you'll be more sensible about this whole thing andwould you \emph{please} take a ten percent commission -''

``Shut up, you,'' said George or Fred.

``For God's sake, you went after a troll for me and Fred had his ribsbroken!''
They both just shook their heads. Harry had stayed behind when they'dtold him to run, and stepped forward to distract the troll from eatingGeorge. Harry was the kind of person, they knew, who'd think thatsomething like that didn't cancel out what he owed the Weasley twins,that his own deed wasn't properly commensurate. But what the Weasleysknew, and Harry wouldn't understand until he was older, was that itmeant that nothing was owed, or ever could be owed between them. It wasa strange kind of selfishness, they thought, that Harry could understandkindness within himself - never dreaming of asking of money from anyonehe'd helped more than they'd helped him, or calling that a debt - whilebeing apparently unable to conceive that others might want to act thesame way toward \emph{him} .

``Remind me to buy you a copy of the Muggle novel \emph{AtlasShrugged,}'' the sourceless voice said. ``I'm starting to understandwhat sort of person can benefit from reading it.''

\begin{center}\rule{3in}{0.4pt}\end{center}

\emph{Monday, April 20th, 7:00pm.}
It happened without any intervention or sign from the Head Table, as thestudents had finished their subdued dinner; it happened with nopermission or forgiveness asked from the Professors or the Headmaster.
Shortly after the dessert dishes had appeared, a student stood up fromthe Slytherin Table and calmly made his way, not to the front of theHead Table, but toward the opposite side of the Four Tables of Hogwarts.A few whispers broke out at the sight of the white-blonde short-croppedhair, as Draco Malfoy stood there, silently regarding all of Hogwarts.Draco Malfoy had said almost nothing since his surprise return. TheSlytherin had condescended neither to confirm nor deny that he hadreturned because, with Hermione Granger dead at his family's hand, he nolonger had anything to fear.
Then Draco Malfoy took up a spoon in one hand, and a glass of water inthe other, and began tapping, producing a clear ringing sound.

\emph{Ting.}

\emph{Ting.}

\emph{Ting.}
It produced more excited babble at first. At the Head Table, the variousProfessors looked in puzzlement toward the Headmaster in his greatchair, but the Headmaster gave no sign, and so the faculty did nothing.
Draco Malfoy continued tapping the spoon upon his glass, until the roomfell silent, waiting.
Then another student arose from the Ravenclaw table, and made his way towhere Draco Malfoy was standing, turning to face Hogwarts at his side.Breaths were drawn in surprise; those two should have been the bitterestof enemies -

``I, and my Father, the Lord of the Noble and Most Ancient House ofMalfoy,'' Draco Malfoy said in a clear voice, ``have come to realizethat there are ill forces at work in Hogwarts. That these ill forces,did wish Hermione Granger harm. That Hermione Granger was perhapscompelled, against her will, to raise her hand against our House; orperhaps she and I were both Memory-Charmed. We now say that whoeverdared use the heir of Malfoy so, is the enemy of House Malfoy, upon whomwe shall have our vengeance. And that honor be served, we have returnedall moneys taken from House Potter, and canceled all debt.''
Then Harry Potter spoke. ``House Potter acknowledges that it was anhonest mistake, and holds House Malfoy no ill will. We believe andpublicly say that House Malfoy was not at fault in Hermione Granger'sdeath. Whoever harmed Hermione Granger is the enemy of House Potter,upon whom we shall have our vengeance. Both of us.''
Then Harry Potter began to walk back to the Ravenclaw table, and thebabble of sheer, utter, reality-crashing bewilderment began to explode -
Draco Malfoy resumed tapping his spoon against his waterglass, creatinga clear ringing chime.

\emph{Ting.}

\emph{Ting.}

\emph{Ting.}
And other students arose, from other tables, making their way to whereDraco Malfoy stood, arranging themselves at his side, or behind him, orbefore him.
There was a dread silence in the Great Hall, a sense of the worldshifting, of realigning Powers, almost tangible in the air.

``My father, Owen Greengrass, with the consent and full backing of mymother, the Lady of the Noble and Most Ancient House of Greengrass,''Daphne Greengrass spoke.

``And my forefather, Charles, of the House of Nott,'' said the formerLieutenant Nott, once Theodore of Chaos, now standing behind DracoMalfoy.

``And my grand-aunt, Amelia, of the House of Bones, also Director of theDepartment of Magical Law Enforcement,'' said Susan Bones, who stoodanext Daphne Greengrass, beside whom she had fought.

``And my grandmother, Augusta, of the Noble and Most Ancient House ofLongbottom,'' said Neville Longbottom, who had returned for this onenight.

``And my father, Lucius, the Lord Malfoy, of the Noble and Most AncientHouse of Malfoy!''

``Together with Alanna Howe constituting a majority of the HogwartsBoard of Governors!'' Daphne Greengrass said clearly. ``Have, to ensurethe safety of all students, including their own children, passed thefollowing Educational Decrees upon the Hogwarts School of Witchcraft andWizardry!''

\begin{center}\rule{3in}{0.4pt}\end{center}

``First!'' Daphne said. Daphne was trying to keep her trembling undercontrol, as she faced the Four Houses at the forefront of the five.There was only so far her parents' lessons in speech-making could takeher. Daphne's eyes darted down quickly to her hand, upon which, writtenwith a quill in faint red ink, cues to her lines had been written.
``Students are not to go anywhere alone, not even to the toilets! Youwill travel in groups of at least three, and every group must have asixth-year or seventh-year student!''

``Second!'' Susan Bones said from behind her, voice almost firm. ``Tofurther ensure the students' safety, nine Aurors have been dispatched toHogwarts to form an Auxiliary Protective Force!'' Susan took a small,round glass object from within her robes, one of the communicators thatthe DMLE used, which they'd all been given. Susan raised it to her mouthand said, her voice now higher, ``Auror Brodski, this is Susan Bones.
\emph{Enter!}''
The doors to the Hall slammed open, and in marched nine Aurors in thereinforced leather gear they used when on duty. At once they spread out,two Aurors taking up station by each of the four tables, and the lasttook up watch at the Head Table. There were more gasps.

``Third!'' said Draco Malfoy, his voice commanding. Malfoy hadapparently memorized his own lines, since there was nothing written onhis hand that Daphne could see. ``In the face of a common enemy who doesnot balk at killing students from any House, the four Houses of Hogwartsmust come together and act as one! To emphasize this, the House Pointssystem is temporarily suspended! \emph{All} Professors will encouragesolidarity between Houses, by decree of the Hogwarts Board ofGovernors!''

``Fourth!'' recited Neville Longbottom. ``All students not already inthe Defense Professor's after-school classes, will receive specialtraining in self-defense by Auror instructors!''

``Fifth!'' Theodore Nott yelled in a menacing tone. ``All fighting inthe corridors or anywhere outside of Defense lessons will be dealt withseverely! Fight together or don't fight at all!''

``Sixth!'' said Daphne Greengrass, and took a deep breath. When she'dfound out what was planned, she'd made her own little extra request toMother through the Floo. Even with Lucius Malfoy going along with AmeliaBones - a thought her mind was still having trouble grasping - theGreengrass swing vote had still been vital, since Jugson and his ownfaction had refused to back Malfoy. Not to mention that Bones didn'ttrust Malfoy, and Malfoy didn't trust Bones. So Mother had demanded, andthe Greengrasses had received - ``Since Memory Charms have been used onstudents without setting off wards, it is possible that someone on theHogwarts faculty may be implicated. Therefore! The Auxiliary Protectiveforce reports directly to my father, Lord Greengrass!'' And this partwas only symbolic, she knew, there'd be no reason anyone wouldn't justcontact the Aurors directly; but it might turn into more, someday, whichwas why she'd asked Mother to demand it - ``And if anyone wants toreport something to the Auxiliary Protectors, they can talk to theAurors, or go through \emph{me} -'' Daphne's arm swept behind her toindicate the gathered students. ``The duly appointed President of theAuxiliary Protective Special Committee!''
And Daphne paused dramatically. They'd all rehearsed this part.

``We don't know who the enemy is,'' said Neville, whose voice did notsqueak.

``We don't know what the enemy wants,'' said Theodore, still lookingmenacing.

``But we know who the enemy is attacking,'' said Susan, as fierce aswhen she'd taken on three seventh-year students.

``The enemy is attacking Hogwarts students,'' said Draco Malfoy, clearand commanding, like all this was his natural element.

``And Hogwarts,'' spoke Daphne of Greengrass, feeling her blood burnlike it never had before in her life, ``is going to *fight back.''