\chapter{Precautionary Measures, Pt 2}
Harry stood, panting, in the midst of a brief wasted circle amid theforest, more destruction than a first-year should have been able toreach, by himself. The Severing Charm wouldn't bring down a tree, sohe'd started partially Transfiguring cross-sections through the wood. Ithadn't let out what was inside him, bringing down a small circle oftrees hadn't made him feel any better, all the emotions were still therebut while he was destroying trees he at least wasn't thinking about howthe feelings couldn't be let out.
After Harry had run out of available magic he'd started tearing offbranches with his bare hands and snapping them. His hands were bleeding,though nothing that Madam Pomfrey couldn't fix in the morning. Only Darkmagic left permanent scars on wizards.
There came a sound of something moving in the woods, like the hoofbeatsof a horse, and Harry whirled, his wand rising once more; some part ofhis magic had returned while he was working with his hands. It occurredto him for the first time that he was out in the Forbidden Forest alone,and making noise.
What emerged into the moonlight was not the unicorn Harry had expected,but a creature with a lower body like that of a horse, gleamingwhite-brown beneath the moonlight, and the bare upper chest of a malehuman with long white hair. The moonlight caught the centaur's face, andHarry saw that the eyes were almost as blue as Dumbledore's, halfway tosapphire.
In one hand the centaur held a long wooden spear, with an overlargemetal blade whose edge did not gleam beneath the moonlight; a gleamingedge, Harry had once read, was the sign of a dull blade.

``So,'' the centaur said. His voice was low, powerful and male. ``Hereyou are, surrounded by destruction. I can smell the unicorn's blood inthe air, the blood of something innocent, slain to save oneself.''
A jolt of sudden fear brought Harry into the now, and he said quickly,
``It's not what it looks like.''

``I know. The stars themselves proclaim your innocence, ironicallyenough.'' The centaur took a step toward Harry within the smallclearing, still holding his spear upright. ``A strange word,
\emph{innocence.} It means lack of knowledge, like the innocence of achild, and also means lack of guilt. Only those entirely ignorant canlack all responsibility for the consequences of their actions. He knowsnot what he does, and therefore can be without harmful intent; so saysthat word.'' The deep voice did not echo in the woods.
Harry's eyes flickered to the spear-tip, and he realized that he shouldhave grabbed his Time-Turner the moment he saw the centaur. Now, ifHarry tried to reach beneath his robes, the spear could strike himbefore then, if the centaur was fast enough. ``I read once,'' Harrysaid, his voice a bit unsteady as he tried to match deep-sounding wordsto deep-sounding words, ``that it's wrong to think of little children asinnocent, because not knowing isn't the same as not choosing. Thatchildren do little harms to each other with schoolyard fights, becausethey don't have the power to do great harm. And some adults do greatharm. But the adults who don't, aren't they more innocent than children,not less?''

``The wisdom of wizards,'' the centaur said.

``Muggle wisdom, actually.''

``Of the magicless I know little. Mars has been dim of late, but itgrows brighter.'' The centaur took another step forwards, bringing himalmost within striking distance of Harry.
Harry didn't dare look up to the sky. ``That means Mars is coming closerto the Earth, as both planets go around the Sun. Mars is reflecting thesame amount of sunlight as always, it's just getting nearer to us. Whatdo you mean, the stars proclaim my innocence?''

``The night sky speaks to centaurs. It is how we know what we know. Ordo they not even tell wizards that much, these days?'' A look ofcontempt crossed the centaur's face.

``I\ldots{} tried to look up centaurs, when I was checking outDivination. Most of the authors just ridiculed centaur Divinationwithout explaining why, wizards don't understand argumentative norms, tothem ridiculing an idea or a person feels like casting that idea downjust as much as bringing evidence against it\ldots{} I thought the partabout centaurs using astrology was just more ridicule\ldots{}''

``Why?'' the centaur intoned. His head cocked curiously.

``Because the course of the planets is predictable for thousands ofyears in advance. If I talked to the right Muggles, I could show you adiagram of exactly what the planets will look like from this spot tenyears later. Would you be able to make predictions from that?''
The centaur shook his head. ``From a diagram? No. The light of theplanets, the comets, the subtle shifts in the stars themselves, those Iwould not see.''

``Cometary orbits are also set thousands of years in advance so theyshouldn't correlate much to current events. And the light of the starstakes years to travel from the stars to Earth, and the stars don't movemuch at all, not visibly. So the obvious hypothesis is that centaurshave a native magical talent for Divination which you just, well,
\emph{project} onto the night sky.''

``Perhaps,'' the centaur said thoughtfully. His head lowered. ``Theothers would strike you for saying such a thing, but I have ever soughtto know what I do not know. Why the night sky can foretell the future -that I surely do not know. It is hard enough to grasp the skill itself.All I can say, son of Lily, is that even if what you are saying is true,it does not seem useful.''
Harry allowed himself to relax a little; being addressed as `son ofLily' implied that the centaur thought of him as more than a randomintruder in the forest. Besides, attacking a Hogwarts student wouldprobably bring some kind of huge reprisal upon the non-wizard centaurtribe in the forests, and the centaur probably knew that\ldots{} ``WhatMuggles have learned is that there is a power in the truth, in all thepieces of the truth which interact with each other, which you can onlyfind by discovering as many truths as possible. To do that you can'tdefend false beliefs in any way, not even by saying the false belief isuseful. It might not seem to matter whether your predictions are reallybased on the stars or if it's an innate talent being projected. But ifyou wanted to really understand Divination, or for that matter thestars, the real truth about centaur predictions would be a fact thatmatters to other truths.''
Slowly the centaur nodded. ``So the wandless have become wiser than thewizards. What a joke! Tell me, son of Lily, do the Muggles in theirwisdom say that soon the skies will be empty?''

``Empty?'' Harry said. ``Er\ldots{} no?''

``The other centaurs in this forest have stayed from your presence, forwe are sworn not to set ourselves against the heavens' course. Because,in becoming entangled in your fate, we might become less innocent inwhat is to come. I alone have dared approach you.''

``I\ldots{} don't understand.''

``No. You are innocent, as the stars say. And to slay something innocentto save oneself, that is a terrible deed. One would live only a cursedlife, a half-life, from that day. For any centaur would surely be castout, if he slew a foal.''
The spear made a lightning motion, too fast for Harry's eyes to follow,and smashed his wand out of his hand.
Another powerful blow smashed into Harry's solar plexus, and he wentgasping and retching to the forest floor.
Harry's hand reached up toward his robes, for his Time-Turner, and thespear-butt knocked his hand away, almost hard enough to break fingers,he reached with his other hand and that was knocked away too -

``I am sorry, Harry Potter,'' the centaur said, and then looked up withwidened eyes. The spear spun about and came up, intercepting a redspellbolt. Then the centaur dropped the spear and leaped awaydesperately, a green flash of light went past him and another greenflash of light followed in its wake, then a third green flash hit thecentaur straight-on.
The centaur fell and did not move again.
It took a long time for Harry to catch his breath, to stagger to hisfeet, to pick up his wand, to croak, ``What?''
By that time the sense of doom, of power almost tangible in the air, hadapproached once more.

``P-Professor Quirrell? What are you doing here?''

``Well,'' the man in the black cloak said thoughtfully, " \emph{you}needed to fly into a rage and have a loud tantrum in the ForbiddenForest in the middle of the night, and \emph{I} needed to go justoutside your ability to detect me and keep watch. One does not leave astudent alone in the Forbidden Forest. That should be obvious inretrospect."
Harry stared at the fallen centaur.
The horse-form wasn't breathing.

``You - you \emph{killed} him, that was Avada Kedavra -''

``I do not always understand how other people imagine morality to work,Mr.~Potter. But even I know that on conventional morality, it isacceptable to kill nonhuman creatures which are about to slay a wizardchild. Perhaps you do not care about the nonhuman part, but he was aboutto \emph{kill} you. He was hardly innocent -''
The Defense Professor stopped, looking at Harry, who had raised onetrembling hand to his mouth.

``Well,'' the Defense Professor said then, ``I have made my point, andyou may think on it. Centaur spears can block many spells, but no onetries to block if they see that the spell is a certain shade of green.For this purpose it is useful to know some green stunning hexes. Really,Mr.~Potter, you should understand by now how I operate.''
The Defense Professor came nearer the centaur's body, and Harry took aninvoluntary step back, then another, at the terrible rising sense of
\emph{STOP, DON'T -}
The Defense Professor kneeled and pressed his wand to the centaur'shead.
The wand stayed there for a time.
And the centaur rose, eyes blank, breathing once more.

``Remember nothing of this time,'' the Defense Professor commanded.
``Wander away and forget everything about this night.''
The centaur walked away, the four horse-legs moving in strangesynchrony.

``Happy now?'' the Defense Professor said, sounding rather sardonicabout it.
Harry's brain still felt broken. ``He was trying to \emph{kill} me.''

``Oh, for Merlin's sake - yes, he was trying to kill you. Get used toit. Only boring people never have that experience.''
Harry's voice emerged, hoarse. ``Why - why did he want to -''

``Any number of reasons. I would be lying if I said I'd never consideredkilling you myself.''
Harry stared at where the centaur had wandered into the trees.
His brain still felt half-broken, like an engine misfiring, but Harrydid not see how this could possibly be a good sign.

\begin{center}\rule{3in}{0.4pt}\end{center}
The news of Draco Malfoy nearly being eaten by a horror had beensufficient to summon back Dumbledore from wherever he'd gone, to wakeLord Malfoy and the Lady Greengrass's handsome husband, to bring forthAmelia Bones. The supposed presence of the horror had provokedskepticism even from Dumbledore, and the possibility of False MemoryCharms had been raised. Harry had said (after some internal debate aboutthe consequences of people believing a demon was on the loose) that hedidn't actually remember making the same effort he'd put forth tofrighten the Dementor, the dark thing had just left; which was what youwould expect someone to create as a False Memory, if they hadn'tactually known how Harry had done it. The names of Bellatrix Black,Severus Snape, and Quirinus Quirrell had been mentioned in connectionwith wizards strong enough to subdue everyone present and cast FalseMemory Charms, and Harry had known that Lucius was thinking ofDumbledore. There had been Aurors testifying, and discussions going incircles, and glares of accusation, and cutting remarks at 2AM in themorning. There had been motions, and votes, and consequences.

``Do you believe,'' Headmaster Dumbledore said quietly to Harry, whenall of it was done, and the two of them alone, ``that the Hogwarts youhave wrought is an improvement?''
Harry sat with his elbows on his knees, his face resting on his palms,in the conference room from which all the others had now departed.Professor McGonagall, who did not use a Time-Turner as routinely as thetwo of them, had departed swiftly for her bed.

``Yes,'' Harry answered after too long a hesitation. ``From myperspective, Headmaster, things in Hogwarts are finally, finally normal.This is how things should be, when four children get sent into theForbidden Forest at night. There should be a huge fuss, constablesshowing up, and the responsible party getting sacked.''

``You believe it is good,'' Dumbledore said quietly, ``that the man whoyou call responsible was, as you put it, sacked.''

``Yes, in fact, I do.''

``Argus Filch has served this institution for decades.''

``And when given Veritaserum,'' Harry said tiredly, ``Argus Filchrevealed that he had sent an eleven-year-old boy into the ForbiddenForest, hoping something awful would happen to him, because he thoughtthe boy's father had been responsible for the death of his cat. Thethree other students in Draco's company don't seem to have fazed him. Iwould have argued for jail time, but your concept of jail in thiscountry is Azkaban. I'll also note that Filch was remarkably unpleasantto the children in Hogwarts and I expect the school's hedonic index tobe improved by his departure, not that it matters to you, I suppose.''
The Headmaster's eyes were impenetrable behind the half-moon glasses.
``Argus Filch is a Squib. His work at Hogwarts is all he has. Had,rather.''

``The purpose of a school is not to provide work for its employees. Iknow you probably spent more time around Filch than around anyindividual student, but that shouldn't make Filch's inner experiencesloom larger in your thoughts. Students have inner lives too.''

``You don't care at all, do you Harry?'' Dumbledore's voice was quiet.
``About those you hurt.''

``I care about the innocent,'' Harry said. ``Like Mr.~Hagrid, who you'llnote I argued should not be considered malicious, just oblivious. I wasfine with Mr.~Hagrid working here so long as he didn't take anyone intothe Forbidden Forest again.''

``I had thought that with Rubeus vindicated, he might teach Care ofMagical Creatures after Silvanus departs the position. But much of thatteaching is done in the Forbidden Forest. So that too shall not be, inthe wake of your passage.''
Harry said slowly, ``But - you told us that Mr.~Hagrid has a blind spotwhen it comes to magical creatures threatening wizards. That Mr.~Hagridhad a cognitive deficit and couldn't really imagine Draco and Traceygetting hurt, which was why Mr.~Hagrid didn't see anything wrong withleaving them alone in the Forbidden Forest at night. Was that nottrue?''

``It is true.''

``Then wouldn't Mr.~Hagrid be the worst possible teacher for MagicalCreatures?''
The old wizard gazed down at Harry through the half-moon glasses. Hisvoice was thick when he spoke. ``Mr.~Malfoy himself saw nothing awry. Itwas not so implausible a trick which Argus played, Harry Potter. AndRubeus might have grown into his position. It would have been - allRubeus wished, his one greatest desire -''

``Your mistake,'' Harry said, looking down at his knees, feeling atleast ten percent as exhausted as he'd ever been, ``is a cognitive biaswe would call, in the trade, scope insensitivity. Failure to multiply.You're thinking about how happy Mr.~Hagrid would be when he heard thenews. Consider the next ten years and a thousand students taking MagicalCreatures and ten percent of them being scalded by Ashwinders. No onestudent would be hurt as much as Mr.~Hagrid would be happy, but there'dbe a hundred students being hurt and only one happy teacher.''

``Perhaps,'' the old wizard said. ``And your own error, Harry, is thatyou do not feel the pain of those you hurt, once you have done yourmultiplication.''

``Maybe.'' Harry went on staring at his knees. ``Or maybe it's worsethan that. Headmaster, what does it mean if a centaur doesn't like me?''
\emph{What does it mean when a member of a race of magical creaturesknown for Divination gives you a lecture on people who are ignorant ofconsequences, apologizes, and then tries to stab you with a spear?}

``A centaur?'' the Headmaster said. ``When did you - ah, theTime-Turner. You are the reason why I could not travel back to beforethe event, on pain of paradox.''

``Am I? I guess I am.'' Harry shook his head distantly. ``Sorry.''

``With very few exceptions,'' Dumbledore said, ``centaurs do not likewizards, at all.''

``This was a bit more specific than that.''

``What did the centaur say to you?''
Harry didn't reply.

``Ah.'' The Headmaster hesitated. ``Centaurs have been wrong many times,and if there is anyone in the world who could confuse the starsthemselves, it is you.''
Harry looked up, and saw the blue eyes once more gentle behind thehalf-circle glasses.

``Do not fret too much about it,'' said Albus Dumbledore.

\begin{center}\rule{3in}{0.4pt}\end{center}

\emph{You have reached the in-progress point of the story,}\\
\emph{which is still being written.}

\emph{Making an account at fanfiction dot net will enable you to add anemail Story Alert;}\\ \emph{or visit HPMOR dot com for one-click emailsubscription with no account required,}\\ \emph{plus links to an RSSfeed, Twitter feed, iPhone app, Facebook page,}\\ \emph{and other meansof being notified when the story updates.}

\emph{The story currently has one more one-shot update left to go,\\ andafter that the long final arc which will wrap everything up with noloose ends,\\ which I fondly hope to get done before the end of 2014.}

\emph{Further information appears at \textbf{HPMOR dot com} .}

\emph{Continuing discussion of this fic occurs at the \textbf{/r/HPMORsubreddit}}\\ \emph{(currently with 5,149 Bayesian Conspirators)}

\emph{If you are incredibly good at math and would like to invent newbasic math}\\ \emph{relating to decision theories consistent underreflection, for use in self-modifying AI,}\\ \emph{please check out theMachine Intelligence Research Institute,}\\ \emph{my employer, at
\textbf{intelligence dot org} .}

\emph{If you wish to acquire improved rationality skills in your ownlife,}\\ \emph{please visit the Center for Applied Rationality at
\textbf{rationality dot org} ,}\\ \emph{and consider attending one oftheir workshops.}

\emph{A forum for general discussion of human rationality, along withmany fine essays}\\ \emph{and two years of daily rationalityblogging onmy part, may be found at \textbf{lesswrong dot com} .}\\ \emph{Pleasekeep in mind that LessWrong dot com is an open forum, on theInternet,}\\ \emph{and that not everything someone posts there isrepresentative of my or anyone else's opinion.}

\emph{\textbf{Progress Reports} (not a story update, a note on writingprogress)\\ appear on the \textbf{1st of each month} at \textbf{5pmPacific Time\\} at \textbf{hpmor dot com slash notes.}}