\chapter{Roles, Pt 7}

\emph{A/N: For those who have not read canon: The wooden sign hassomewhat changed, but the inscription here is the same as in J.K.Rowling's original.}

\begin{center}\rule{3in}{0.4pt}\end{center}

\emph{The fourth meeting:\\ (4:38pm, April 17th, 1992)}

The man wearing the worn, warm coat, with three faint scars etchedforever into his cheek, observed Harry Potter as closely as he couldwhile the boy looked around politely at the rows of cottages. Forsomeone whose best friend had died yesterday, Harry Potter seemedstrangely composed, though not in any way reminiscent of unfeelingness,or normality. \emph{I don't wish to talk about that,} the boy had said,\emph{with you or anyone.} Saying `wish' and not `want', as though toemphasize that he was able to use grownup words and make grownupdecisions. There had been only one thing Remus Lupin had thought of thatmight help, after he'd received the owls from Professor McGonagall andthat strange man Quirinus Quirrell.

``There's a lot of empty houses,'' the boy said, glancing around again.

Godric's Hollow had changed, in the decade since Remus Lupin had been afrequent visitor. Many of the old, peaked cottages looked deserted, withgreen leafy vines growing across their windows and their doors. Britainhad contracted noticeably, in the aftermath of the Wizarding War, havinglost not only the dead but the fled. Godric's Hollow had been hard-hit.And afterward still more families had moved elsewhere, to Hogsmeade ormagical London, the deserted houses too uncomfortable a reminder.

Others had remained. Godric's Hollow was older than Hogwarts, older thanGodric Gryffindor whose name it had taken, and there were families whichwould reside here until the end of the world and its magic.

The Potters had been one such family, and would be again, if the lastPotter so chose.

Remus Lupin tried to explain all that, simplifying it as best he couldfor the young boy. The Ravenclaw nodded thoughtfully and said nothing,as though he had understood it all without need of questions. Perhapsthat was so; the child of James Potter and Lily Evans, the Head Boy andHead Girl of Hogwarts, would hardly be stupid. The child had certainlyseemed highly intelligent, for the little time that they had spoken inJanuary, though at that time Remus had done most of the talking.

(There was also that business with the Wizengamot which Remus had heardrumors about, but Remus didn't believe a single word of that, any morethan he'd believed it about James betrothing his son to Molly'syoungest.)

``There's the monument,'' Remus said, pointing ahead of them.

\begin{center}\rule{3in}{0.4pt}\end{center}

Harry walked beside Mr.~Lupin toward the black marble obelisk, thinkingsilently. It seemed to Harry that this adventure was essentiallymisguided; he had no use for grief counseling, that was not Harry'schosen path. So far as Harry was concerned, the five stages of griefwere Rage, Remorse, Resolve, Research, and Resurrection. (Not that theusual `five stages of grief' had any experimental evidence whatsoeverthat Harry had ever heard about.) But Mr.~Lupin had seemed too sincereto refuse; and visiting James and Lily's home was something Harry felthe ought not to turn down. So Harry walked, feeling oddly detached;walking silently through a play whose script he was not interested inreading.

Harry had been told that he wasn't to wear the Cloak of Invisibility forthis journey, so that Mr.~Lupin could keep track of him.

Harry was morally certain that Dumbledore, or both Dumbledore andMad-Eye Moody, were following them invisibly to see if anyone tried forthe bait. There was no way Harry would have been let out of Hogwartswith only Remus Lupin for a guard. Harry didn't expect anything tohappen, though. He'd seen nothing to contradict the hypothesis that allthe danger centered on Hogwarts and only Hogwarts.

As the two of them walked closer toward the center of town, the marbleobelisk transformed into -

Harry drew in a breath. He'd been expecting a heroic pose of JamesPotter with wand leveled against Lord Voldemort, and Lily Potter witharms outstretched in front of the crib.

Instead there was a man with untidy hair and glasses, and a woman withher hair let down and a baby in her arms, and that was all.

``It looks very\ldots{} normal,'' Harry said, feeling an odd catch inhis throat.

``Madam Longbottom and Professor Dumbledore put their foot down hard,''said Mr.~Lupin, who was looking more at Harry than at the monument.``They said that the Potters should be remembered as they had lived, notas they had died.''

Harry looked at the statue, thinking. Very strange, to see himself as ababy of stone, with no scar upon his forehead. It was a glimpse at analternate universe, one where Harry James Potter (no Evans-Verres to hisname) became an intelligent but ordinary wizarding scholar, maybe Sortedinto Gryffindor like his parents. A Harry Potter who grew up a properyoung wizard, knowing little of science for all that his mother wasMuggleborn. Ultimately changing\ldots{} not much. James and Lilywouldn't have raised their son with what Professor Quirrell would havecalled \emph{ambition} and what Professor Verres-Evans would have called\emph{the common endeavor.} His birth parents would have loved him verymuch, and that would not have been much help to anyone in the worldexcept Harry. If someone had undone their death -

``You were their friend,'' Harry said, turning to look at Lupin. ``For along time, since you were children.''

Mr.~Lupin nodded silently.

Professor Quirrell's voice resounded in Harry's approximate memory:\emph{The most likely difference is not that you care more. Rather it isthat, being a more logical creature than they, only you are aware thatthe role of Friend ought to require this of you\ldots{}}

``When Lily and James died,'' Harry said, ``did you think at all ofwhether there might be some magical way to get them back? Like Orpheusand Eurydice? Or the, what was it, Elrin brothers?''

``There is no magic which can undo death,'' Mr.~Lupin said quietly.``There are some mysteries which wizardry cannot touch.''

``Did you do a mental check of what you thought you knew, how youthought you knew it, and how high the probability was of thatconclusion?''

``What?'' said Mr.~Lupin. ``Could you repeat that, Harry?''

``I'm saying, did you think about it anyway?''

Mr.~Lupin shook his head.

``Why not?''

``Because it was already done, and over,'' Remus Lupin said gently.``Because wherever James and Lily are now, they would wish me to act forthe sake of the living, not the dead.''

Harry nodded silently. He'd been pretty sure of the answer to thatquestion before he'd asked. He'd already read that script. But he'dasked anyway, just in case Mr.~Lupin had spent a week obsessing aboutit, because Harry could have been wrong.

The soft voice of the Defense Professor seemed to speak in Harry's mind.\emph{Surely, if Lupin truly cared, he would not need specialinstruction for something as simple as thinking for five minutes beforegiving up\ldots{}}

\emph{Yes, he would,} Harry answered the mental voice. \emph{Humanbeings wouldn't suddenly obtain a skill like that just because theycared. I learned about it because I'd read library books, produced by ahuge scientific edifice -}

And that other part of Harry said, in that soft voice, \emph{But thereis also another hypothesis, Mr.~Potter, and it fits the data in a muchless complicated way.}

\emph{No it doesn't! How would people even know what to pretend, ifnobody had ever cared?}

\emph{They don't know. That is what you observe.}

The two of them walked onward toward a certain house, past a long row ofoccupied wizard cottages and other cottages overgrown with vines.

Coming finally to the house with half its top blown off, and greenleaves growing over into the inside; behind a shoulder-high wild-growinghedge lining the sidewalk, and a narrow metal gate (Mr.~Hagrid hadprobably stepped right over it, being unable to fit through). The gap inthe roof was like a giant mouth had taken a circular bite from thehouse, leaving spines of wood, what had maybe been support beams,sticking out. To the right side a single chimney still stood upright,uneaten by the giant bite, but leaning dangerously without its formersupport. Windows were shattered. Where there should have been a frontdoor were only splinters of wood.

To this place Lord Voldemort had come, \emph{silently, making less noisethan the dead leaves slithering along the pavement\ldots{}}

Remus Lupin put a hand upon Harry's shoulder. ``Touch the gate,''Mr.~Lupin urged.

Harry reached out a hand and did so.

Like a fast-growing flower a sign burst from the tangled weeds in theground behind the gate, a wooden sign with golden letters, and it said:

On this spot, on the night of 31 October 1981,\\ Lily and James Potterlost their lives.

They were survived by their son, Harry Potter,\\ the only wizard ever towithstand the Killing Curse,\\ the Boy-Who-Lived, who brokeYou-Know-Who's power.

This house has been left in its ruined state,\\ as a monument to thePotters,\\ as a reminder of their sacrifice.

In a blank space below the golden letters were written other messages,dozens of them, magical ink that rose to the surface and gleamedbrightly enough to be read before fading and giving way to othermessages.

So my Gideon is avenged.

Thank you, Harry Potter. Fare well wherever you are.

We will always be in the Potters' debt.

Oh James, oh Lily, I am sorry.

I hope you're alive, Harry Potter.

There is always a price.

I wish our last words had been kinder, James. I'm sorry.

There is always a dawn after the night.

Rest well, Lily.

Bless you, Boy-Who-Lived. You were our miracle.

``I guess -'' Harry said. ``I guess that's what people do - instead oftrying to make it better -'' Harry stopped. The thought seemed unworthyof this place. He looked up, and saw Remus Lupin gazing at him with alook so gentle that Harry wrenched his eyes away to the blasted andbroken roof.

\emph{You were our miracle.} Harry had always heard the word `miracle'in the context of how, in the natural universe, there was no such thing.And yet looking at the ruined house, he suddenly knew exactly what theword meant, the note of grace all unexplained, the blessinginexplicable. The Dark Lord had almost won, and then in one night allthe darkness and terror had ended, salvation without justification, asudden dawn from out of the darkness and even now nobody knew \emph{why}-

If Lily Potter had lived beyond her confrontation with Lord Voldemort,she would have felt that way when she saw her baby alive, afterward.

``Let's go,'' whispered the baby boy, ten years later.

They went.

The graveyard's entrance was guarded by a lockless gate of the sort thatkept out animals, with a place to stand while you moved the door fromone side of the standing-place to the other. Remus took out his wand(Harry was already holding his) and there was a brief blur as theystepped through.

Some of the stones rising up from the ground looked as old as the wallin Oxford that his father had said was around a thousand years old.

\emph{Hallie Fleming,} said the first stone that Harry saw, in a carvingalmost invisibly faded with the erosion of time. \emph{Vienna Wood,}said another.

It had been a long time since Harry had visited a graveyard. His mindhad still been childlike the last time he'd come to one, long beforehe'd seen within Death's shadow. Coming here now was\ldots{} strange,and sad, and puzzling, and \emph{this has been happening for so long,why haven't wizards tried to stop it, why aren't they putting all theirstrength into that like Muggles do with medical research, only more so,wizards have more reason to hope\ldots{}}

``The Dumbledores lived in Godric's Hollow too?'' Harry said, as theywalked past a pair of relatively new stones saying \emph{KendraDumbledore} and \emph{Ariana Dumbledore.}

``For a long, long time,'' Mr.~Lupin said.

They walked further into the graveyard, far toward the end, past manydeaths that had been mourned.

Then Mr.~Lupin pointed at a linked double headstone, of marble stillwhite and unaged.

``Are there going to be messages there?'' Harry said. He didn't want todeal any more with the way that other people dealt with death.

Mr.~Lupin shook his head.

They walked toward the linked white stones.

And stood before -

``What is this?'' Harry whispered. ``Who\ldots{} \emph{who wrotethis?}''

JAMES POTTER\\ BORN 27 MARCH 1960\\ DIED 31 OCTOBER 1981

``Wrote what?'' said Mr.~Lupin, puzzled.

LILY POTTER\\ BORN 30 JANUARY 1960\\ DIED 31 OCTOBER 1981

" \emph{This!} " Harry cried. ``The \emph{inscription!}'' There weretears welling up in Harry's eyes, at the brightness out of place andunexplained, the touch of grace where no grace should have been, themysterious blessing, tears welling up at

THE LAST ENEMY THAT SHALL BE DESTROYED IS DEATH

``That?'' Mr.~Lupin said. ``That's the\ldots{} motto, I suppose youcould call it, of the Potters. Though I don't think it was eversomething as formal as that. Just a saying handed down from long, longago\ldots{}''

``This - that -'' Harry scrambled down to kneel beside the grave,touched the inscription with a trembling hand. " \emph{How?} Things likethat can't just be, be \emph{genetic} -"

Then Harry saw what tears had blurred, the faint carving of a line,within a circle, within a triangle.

The symbol of the Deathly Hallows.

And Harry understood.

``They tried,'' Harry whispered.

\emph{The three Peverell brothers.}

\emph{Had they lost someone precious to them, was that where it hadbegun?}

``With all their lives, they tried, and they made progress -''

\emph{The Cloak of Invisibility, that could defeat the Dementors'sight.}

``- but their research wasn't finished -''

\emph{Hiding from Death's shadow is not defeating Death itself. TheResurrection Stone couldn't really bring anyone back. The Elder Wandcouldn't protect you from old age.}

``- so they passed on the mission to their children, and theirchildren's children.''

\emph{Generation after generation.}

\emph{Until it came to me.}

Could Time echo like that, rhyming, between this far into the future,and that far in the past? It \emph{couldn't} be coincidence, could it?Not this message, not in this place.

\emph{My family.}

\emph{You really were, my mother and my father.}

``It doesn't mean resurrecting the dead, Harry,'' Mr.~Lupin said. ``Itmeans accepting death, and so being beyond death, mastering it.''

``Did James tell you that?'' Harry said, his voice strange.

``No,'' said Mr.~Lupin, ``but -''

``Good.''

Harry rose up slowly from where he had been kneeling, feeling as thoughhe were pushing up a sun upon his shoulders, raising the dawn above thehorizon. \emph{\\}

\emph{Of} course \emph{other wizards have tried. I am not unique. I wasnever alone. These feelings in my heart, they're not so special, not inthe wizard world or the Muggle one.}

``Harry, your wand!'' There was a sudden excitement in Mr.~Lupin'svoice, and when Harry raised his wand to look at it closely, he saw thatit was gleaming ever so faintly with a silver light, welling out of thewood.

``Cast the Patronus Charm!'' urged Mr.~Lupin. ``Try casting it again,Harry!''

\emph{Oh, right. So far as Mr.~Lupin knows, I can't -}

Harry smiled, and even laughed a little. ``I'd better not,'' Harry said.``If I tried to cast the spell in this state of mind, it'd probably killme.''

*``What?*'' said Mr.~Lupin. ``The Patronus Charm doesn't do that!''

Harry James Potter-Evans-Verres raised his left hand, still laughing,and wiped away some more tears.

``You know, Mr.~Lupin,'' Harry said, ``it really takes a \emph{baroque}interpretation to think that somebody would be walking around, ponderinghow death is just something we all have to accept, and communicate theirstate of mind by saying, `The last enemy that shall be destroyed isdeath.' Maybe someone else thought it sounded poetic and picked up thephrase and tried to interpret it differently, but whoever said it firstdidn't like death much.'' Sometimes it puzzled Harry how most peopledidn't seem to even \emph{notice} when they were twisting somethingaround to the 180-degree opposite of its first obvious reading. Itcouldn't be a raw brainpower thing, people could see the obvious readingof most other English sentences. ``Also `shall be destroyed' refers to achange of future state, so it can't be about the way things are now.''

Remus Lupin was staring at him with wide eyes. ``You certainly are Jamesand Lily's child,'' the man said, sounding rather shocked.

``Yes, I am,'' Harry said. But that wasn't enough, he had to dosomething more, so Harry raised his wand in the air and said, his voiceas steady as he could make it, ``I am Harry James Potter-Evans-Verres,the son of Lily and James, of the house of Potter, and I accept myfamily's quest. Death is my enemy, and I will defeat it.''

\emph{Thrayen beyn Peverlas soona ahnd thrih heera toal thissoom Dathbey yewoonen.}

``What?'' Harry said aloud. The words had popped up into his stream ofconsciousness as though from his own thoughts, unexplained.

``What was that?'' said Remus Lupin at the same time.

Harry turned, scanning the graveyard, but he didn't see anything. Besidehim, Mr.~Lupin was doing the same.

Neither of them noticed the tall stone worn as though from a thousandyears of age, upon it a line within a circle within a triangle glowingever so faintly silver, like the light which had shone from Harry'swand, invisible at that distance beneath the still-bright Sun.

\begin{center}\rule{3in}{0.4pt}\end{center}

\emph{Some time later:}

``Thank you again, Mr.~Lupin,'' Harry said, the tall, faintly scarredman was about to depart once more. ``Though I really wish you hadn't -''

``Professor Dumbledore said that I was to portkey us back to Hogwarts ifanything unusual happened, whether or not it seemed like an attack,''Mr.~Lupin said firmly. ``Which is eminently sensible.''

Harry nodded. And then, having carefully saved this question for last,``Do you have any idea of what the words meant?''

``If I did, I wouldn't tell you,'' Mr.~Lupin said, looking rathersevere. ``Certainly not without Professor Dumbledore's permission. I canunderstand your eagerness, but you should not go trying to uncover anyancestral secrets of the Potters until you are an adult. That meansafter you've passed your NEWTs, Harry, or at least your OWLs. And Istill think you've picked up entirely the wrong idea of what your familymotto is meant to say!''

Harry nodded, sighing internally, and bid Mr.~Lupin farewell.

\begin{center}\rule{3in}{0.4pt}\end{center}

Harry went back through Hogwarts, to the Ravenclaw Tower, feelingstrange, and strengthened. He would not have expected any of that, butit had been all to the good.

He was passing through the Ravenclaw common room, on the way to hisdorm.

That was when the shining creature came to him, gleaming soft whitebeneath the candlefires of the Ravenclaw common room, as it slitheredout from nowhere, the silver snake.

\begin{center}\rule{3in}{0.4pt}\end{center}

\emph{Þregen béon Pefearles suna and þrie hira tól þissum Déað béogewunen.}

Three shall be Peverell's sons and three their devices by which Deathshall be defeated.

\begin{itemize}\itemsep1pt\parskip0pt\parsep0pt\item  Spoken in the presence of the three Peverell brothers,\\ in a small  tavern on the outskirts of what would later be called Godric's Hollow.\end{itemize}