\chapter{Roles, Pt 8}
For the second time that day, Harry's eyes filled with tears. Heedlessof the puzzled eyes of the Ravenclaws in the common room, he reached outto the silver creature which Draco Malfoy had sent, cradling it in hisarms like a live thing; and stumbled off in the direction of his dormroom, heading half-blindly for the bottom of his trunk, as the silversnake waited silently in his arms.

\begin{center}\rule{3in}{0.4pt}\end{center}

\emph{The fifth meeting: 10:12am, Sunday, April 19th.}
The debtor's meeting which Lord Malfoy had demanded from Harry Potter,who owed Lucius Malfoy a debt of some 58,203 Galleons, was held withinthe Gringotts Central Bank, in accordance with the laws of Britain.
There had been some pushback from Chief Warlock Dumbledore, trying toprevent Harry Potter from leaving the security of Hogwarts (a phrasethat caused Harry Potter to raise his fingers and silently make quotemarks in the air). For his own part, the Boy-Who-Lived had seeminglypondered quietly, and then assented to the meeting, strangely compliantin the face of his enemy's demand.
The Headmaster of Hogwarts, who acted as Harry Potter's legal guardianin the eyes of magical Britain, had overruled his ward's assent.
The Debts Committee of the Wizengamot had overruled the Headmaster ofHogwarts.
The Chief Warlock had overruled the Debts Committee.
The Wizengamot had overruled the Chief Warlock.
And so the Boy-Who-Lived had departed under the heavy guard of Mad-EyeMoody and an Auror trio for the Gringotts Central Bank; with Moody'sbright-blue eye rotating wildly in every direction, as though to signalto any possible attacker that he was On Guard and Constantly Vigilantand would cheerfully incinerate the kidneys of anyone who sneezed in thegeneral direction of the Boy-Who-Lived.
Harry Potter watched more keenly than before, as they marched throughthe wide-open front doors of Gringotts, beneath the motto \emph{FortiusQuo Fidelius} . On Harry's last three visits to Gringotts he had merelyadmired the marble pillars, the gold-burning torchlights, thearchitecture not quite like the human parts of magical Britain. Sincethen had come the Incident at Azkaban and other things; and now, on hisfourth visit, Harry was thinking about the Goblin Rebellions andgoblins' ongoing resentment at not being allowed to own wands andcertain facts which hadn't been in the first-year History textbook,which Harry had guessed at by pattern-matching and which ProfessorFlitwick had confirmed in a very quiet voice. Lord Voldemort had killedgoblins as well as wizards - an incredibly stupid move on LordVoldemort's part, unless Harry was really missing something - but whatgoblins thought of the Boy-Who-Lived, Harry had no idea. Goblins had areputation for paying what they owed and taking what they thought owedthem, along with a reputation for interpreting those accounts in asomewhat prejudiced fashion.
Today, the guards standing upright in armor at regular intervals aroundthe bank were staring at the Boy-Who-Lived with blank faces, and glaringat Moody and the Aurors with flashes of bitter contempt. At the standsand counters of the bank's foyer, goblin tellers stared with equalcontempt at the wizards whose hands they were filling with Galleons; oneteller smiled a sharp-toothed grin at a witch who was looking angry anddesperate.

\emph{If I understand human nature correctly - and if I'm right that allthe humanoid magical species are genetically human plus a heritablemagical effect - then you're not likely to become friends with a wizardjust because I'm polite to you, or say that I'm sympathetic. But}
\emph{I wonder if you would back the Boy-Who-Lived in a bid to overthrowthe Ministry, if I promised to revoke the Wand Law afterward\ldots{} orif I quietly gave you wands, and spellbooks, in exchange for yoursupport\ldots{} is that why the secret of wand-making is restricted topeople like Ollivander? Though if you really are human, just plainhuman, then the goblin nation probably has its own internal horrors, itsown Azkabans, for that is also human nature; in which case sooner orlater I must overthrow or reform your own government as well. Hm.}
An aged goblin appeared before them, and Harry inclined his head withcareful courtesy, a gesture that the aged goblin returned with an abrupthalf-nod. There was no wild train ride; instead the aged goblin usheredthem into a short hallway that terminated in a small waiting room, withthree goblin-sized benches and one wizard-sized chair, within whichnobody sat.

``Do not sign anything that Lucius Malfoy gives you,'' Mad-Eye Moodysaid. " \emph{Nothing,} do you understand me, lad? If Malfoy hands you acopy of \emph{The Wonderful Adventures of the Boy-Who-Lived} and asksyou for an autograph, tell him that you've sprained a finger. Don't pickup a quill for a single second while you're in Gringotts. If someonehands you a quill, break the quill and then break your own fingers. Do Ineed to explain further, son?"

``Not particularly,'' Harry said. ``We also have lawyers in MuggleBritain, and they'd think your lawyers are cute.''
A short time later Harry Potter handed his wand over to an armoredgoblin guard who frisked him with all manner of interesting-lookingprobes, and gave his pouch to Moody to keep.
And then Harry stepped through another door, and a brief waterfall ofThief's Downfall, which evaporated from his skin as soon as he steppedout.
On the other side of the door was a larger room, richly paneled andappointed, with a great golden table stretching across it; two hugeleather chairs on one side of the table, and a small wooden stool on theother, the debtor's perch. Two goblins in full armor, wearing ornateearpieces and glasses, stood watch around the room. Neither side wouldhave wands or any other device of magic, and the goblin guards wouldattack immediately if anyone dared to use wandless magic within thispeaceable meeting supervised by Gringotts Bank. The ornate earpieceswould prevent the goblin guards from hearing the conversation unlessdirectly addressed, the eyepieces would leave the wizards' faces asblurs. It was, in short, something along the lines of \emph{actual}security, at least if you were an Occlumens.
Harry climbed up onto his uncomfortable wooden stool, thinking
\emph{Subtle} in a tone of some mental sarcasm, and awaited hiscreditors.
It was only a brief interval later, much shorter than the time a debtorcould legally be made to wait, when Lucius Malfoy entered into the room,taking up his leather chair with motions worn smooth by practice. Hissnake-headed cane was missing from his hands, his long white manedrifted behind him the same as ever, his face could not be read.
Quietly following behind him was a young boy with white-blonde hair, nowwearing black robes far finer than any Hogwarts uniform, who followed inhis father's footsteps with a controlled face. A boy who was alsoHarry's creditor to the tune of forty Galleons, and also of HouseMalfoy, and therefore, technically, covered by the Wizengamot resolutionenabling this meeting.

\emph{Draco.} Harry didn't say it aloud, didn't let his own expressionchange. He could not think of what to say. Not even \emph{I'm sorry}seemed appropriate. Harry hadn't dared say any of that to Draco'sPatronus either, when they had set up this meeting in a few briefexchanges; and not only because Lucius might be listening. It had beenenough to know that Draco's happy thought was still happy, and that hehad still been able to want Harry to know it.
Lucius Malfoy spoke first, his voice level, his face set. ``I do notunderstand what is happening at Hogwarts, Harry Potter. Would you careto explain it to me?''

``I don't know,'' Harry said. ``If I understood these events I would nothave let them happen, Lord Malfoy.''

``Then answer me this question. \emph{Who} are you?''
Harry gazed evenly at the face of his creditor. ``I'm not You-Know-Who,like you thought I was,'' Harry said. Not being a \emph{complete} idiot,he'd eventually worked out who Lucius Malfoy had thought he was talkingto in front of the Wizengamot. ``Obviously I'm not a normal boy. Equallyobviously, that probably has \emph{something} to do with theBoy-Who-Lived business. But I don't know what, or why, any more than youdo. I asked the Sorting Hat and it didn't know either.''
Lucius Malfoy nodded distantly. ``I could not think of any reason whyyou would pay a hundred thousand Galleons to save a mudblood's life. Noreason save one, which would account for her power and bloodthirstalike; but then she died at the hands of a troll, and yet you lived. Andalso my \emph{son} has told me \emph{much} of you, Harry Potter, which
\emph{did not make the tiniest bit of sense,} I have heard the ravingsof the mad in St.~Mungo's and they were more sensible by far than theevents which my \emph{son} told me under \emph{Veritaserum} that youenacted, and that portion of this \emph{raving lunacy,} which you
\emph{personally carried out,} I would have you explain to me, andnow.''
Harry turned to look at Draco, who looked back at him with a face thatwas screwing up, being controlled, and then tensing up again.

``I'd also,'' Draco Malfoy said in a high and wavering voice, ``like, toknow, why, Potter.''
Harry closed his eyes, and spoke without looking. ``A boy raised byMuggles who thought he was clever. You saw me, Draco, and you thought ofhow very useful it would be if the Boy-Who-Lived, out of all the otherchildren in your year, could be shown the truth of things, if we couldbe friends. And I thought the same thing about you. Only, you and Ibelieved different things were true. Not that I'm saying that there aredifferent truths, I mean, there's different beliefs but there's only onereality, only one universe that can make those beliefs true or false -''

``You lied to me.''
Harry opened his eyes and looked at Draco. ``I would prefer to say,''Harry said, not quite with a steady voice, ``that the things I told youwere true from a certain point of view.''

\emph{``A certain point of view?''} Draco Malfoy looked every bit asangry as Luke Skywalker'd had the right to be, and not in a mood toaccept Kenobi's excuses, either. ``There's a word for things that aretrue from a certain point of view. They're called \emph{lies!}''

``Or tricks,'' Harry said evenly. ``Statements which are technicallytrue but which deceive the listener into forming further beliefs whichare false. I think it's worth making that distinction. What I told youwas a self-fulfilling prophecy; you believed that you couldn't deceiveyourself, so you didn't try. The skills you've learned are real, and itwould have been very bad for you to start fighting against theminternally. People can't make themselves believe that blue is green byan act of will, but they \emph{think} they can, and that can be almostas bad.''

``You \emph{used} me,'' said Draco Malfoy.

``I only used you in ways that made you stronger. That's what it meansto be used by a friend.''

\emph{``Even I know that's not what friendship is!''}
Now Lucius Malfoy spoke again. ``For what purpose? To what end?'' Eventhe elder Malfoy's voice was not quite steady. " *Why?``*
Harry regarded him for a moment, and then turned to Draco. ``Yourfather's probably not going to believe this,'' Harry said. ``But you,Draco, should be able to see that everything which has happened iscompatible with this hypothesis. And that any more cynical hypothesiswouldn't explain why I didn't press you harder when you thought I hadleverage, or why I taught you so much. I thought that the heir of HouseMalfoy, who'd been publicly seen to grab a Muggleborn girl to stop herfalling off the roof of Hogwarts, would be a good compromise candidateto lead magical Britain after the reformation.''

``So you would have me believe,'' Lucius Malfoy said in a thin voice,
``that you are claiming to be mad. Well, let us leave all that aside.Tell me who set that troll on Hogwarts.''

``I don't know,'' Harry said.

``Tell me who you \emph{suspect,} Harry Potter.''

``I have four suspects. One of them is Professor Snape -''

" \emph{Snape?} " Draco burst out.

``The second, of course, is the Defense Professor of Hogwarts, justbecause he's the Defense Professor.'' Harry would have left him out, notwanting to bring Professor Quirrell to the Malfoys' attention if he wasinnocent, but Draco might have called him on that. ``The third, youwouldn't believe me about. The fourth is a catchall category calledEverything Else.'' \emph{And the fifth, Lord Voldemort, I do not think Ishould name to you.}
Lucius Malfoy's face contorted in a snarl. ``Do you think I cannotrecognize bait upon your hook? Tell me about this third possibility,Potter, the one you wish me to believe is the \emph{true} answer, andleave aside games.''
Harry regarded Lord Malfoy steadily. ``I once read a book I wasn'tsupposed to read, and it told me this: Communication is an event thattakes place between equals. Employees lie to their bosses, who, in turn,expect to be lied to. I'm not playing coy, I'm observing that it'ssimply not possible, in our present situation, for me to tell you aboutthe third suspect, and have you believe that my story was anything but alure.''
Draco spoke then. ``It's Father, isn't it?''
Harry gave Draco a startled look.
Draco spoke evenly. ``You suspect that Father sent the troll intoHogwarts to get at Granger, don't you? That's what you're thinking,isn't it!''
Harry opened his mouth to say, \emph{Actually, no,} and then managed tothink ahead and stop himself for once in his life.

``I see\ldots{}'' Harry said slowly. `` \emph{That's} what this is about.Lucius Malfoy publicly says that Hermione won't get away with what she'sd hone, and lo and behold, a troll kills her.'' Harry smiled then, in a waythat bared his teeth. ``And if I deny that here, then Draco, who isn'tan Occlumens, can then testify under Veritaserum that the Boy-Who-Liveddoes \emph{not} suspect Lucius Malfoy of having sent a troll intoHogwarts to kill Hermione Granger, sworn to the Noble House of Potter,whose blood debt was recently purchased for a hundred thousand Galleonset cetera.'' Harry leaned back slightly, though his wooden stool had noback with which to do it properly. ``But now that it's been pointed out,I see that it's very reasonable. Obviously \emph{you} killed HermioneGranger, just like you threatened to do in front of the wholeWizengamot.''

``I did not,'' Lucius Malfoy said, expressionless once more.
Harry bared his teeth again in that non-smile. ``Well then, in
\emph{that} case, there must be someone \emph{else} out there who killedHermione and messed with the Hogwarts wards, the same person who
\emph{earlier} tried to \emph{frame Hermione for Draco Malfoy's murder.}Either you killed Hermione Granger after being paid for her life, or youblamed your son's attempted murder on an innocent girl and took all myfamily's money under false pretenses, one of those two things must betrue.''

``Perhaps \emph{you} killed her in hopes of your money being returned.''Lucius Malfoy had leaned forward, and was staring hard at Harry.

``Then \emph{I} would not have given away my money for her in the firstplace. As you already know. Don't insult my intelligence, Lord Malfoy -no, wait, sorry, you just had to \emph{say} that in case Draco had totestify to it, never mind.''
Lucius Malfoy sat back in his chair and stared.

``I tried to tell you, Father,'' Draco said under his breath, ``butnobody can imagine Harry Potter until they've actually \emph{met}him\ldots{}''
Harry tapped a finger on his cheek. ``So people are starting to figureout the blatantly obvious? I'm surprised, actually. I wouldn't havepredicted that would happen.'' Harry had by now caught the generalrhythm of Professor Quirrell's cynicism and was able to generate itindependently. ``I wouldn't think a newspaper would be able to report ona concept like `Either X or Y must be true, but we don't know which.' Iwould only expect journalists to report stories consisting of series ofatomic propositions, like `X is true', `Y is false', or `X is true and Yis false'. Not more complex logical connectors like `If X is true then Yis true, but we don't know whether X is true'. And all your supportersought to be rapidly switching between `You can't prove that Lord Malfoykilled Granger, it could've been someone else' and `You can't provethere was someone else to frame Granger', so long as it's uncertain theyshould be trying to have it both ways at once\ldots{} wait, don't you
\emph{own} the Daily Prophet?''

``The Daily Prophet,'' Lucius Malfoy said thinly, ``which I certainly donot own, is far too respectable to publish any such scurrilous nonsense.Unfortunately, not all wizards of influence are so reasonable.''

``Ah. Got it.'' Harry nodded.
Lucius glanced at Draco. ``The rest of what he said - was any of itimportant?''

``No, Father, it was not.''

``Thank you, son.'' Lucius returned his gaze to Harry. His voice, whenhe spoke, was something closer to his usual drawl, cool and confident.
``It is possible that I could be persuaded to show you some favor, ifyou admitted before the Wizengamot what you clearly know, that I was notresponsible for this deed. I would be willing to reduce your remainingdebt to House Malfoy quite significantly, or even adjust the terms toallow later repayment.''
Harry regarded Lucius Malfoy steadily. ``Lucius Malfoy. You are nowperfectly aware that Hermione Granger was, in fact, framed using yourson as bait, that she was False-Memory-Charmed or worse, and that HousePotter held nothing against you before that. My counterproposal is thatyou return my family's money, I announce before the Wizengamot thatHouse Potter holds House Malfoy no animus, and we present a united frontagainst whoever's doing this. We decide to screw the roles we'resupposed to play, and ally with each other instead of fighting. It couldbe the one thing the enemy doesn't expect us to do.''
There was a brief silence in the room, except for the two goblin guardswho went on breathing regardless.

``You \emph{are} mad,'' Lucius Malfoy said coldly.

``It's called justice, Lord Malfoy. You cannot possibly expect me tocooperate with you while you are holding the wealth of House Potterunder what you now know to be false pretenses. I understand how itlooked to you at the time, but you know better now.''

``You have nothing to offer me worth a hundred thousand Galleons.''

``Don't I?'' Harry said distantly. ``I wonder. I think it quite probablethat you care more about the long-term welfare of House Malfoy thanabout whichever political issue the last generation's failed Dark Lordmade his personal hobbyhorse.'' Harry glanced significantly at Draco.
``The next generation is drawing its own battle lines and forming newalliances. Your son can be frozen out of that, or he can go straight tothe top. Is that worth more to you than forty thousand Galleons youweren't particularly expecting and don't particularly need?'' Harrysmiled thinly. ``Forty thousand Galleons. Two million Muggle poundssterling. Your son knows some things about the size of the Muggleeconomy that might surprise you. They'd find it amusing, that the fateof a country was revolving around two million pounds sterling. They'dthink it was cute. And I think much the same, Lord Malfoy. This isn'tabout me being desperate. This is about you getting a fair chance to befair.''

``Oh?'' said Lord Malfoy. ``And if I refuse your fair chance, whatthen?''
Harry shrugged. ``Depends what sort of coalition government gets puttogether without the Malfoys. If the government can be reformedpeacefully and it would disturb the peace to do otherwise, I'll pay youthe money out of petty cash. Or maybe the Death Eaters will be retriedfor past crimes and executed as a matter of justice, as a result of duelegal process, of course.''

``You truly are mad,'' Lucius Malfoy said quietly. ``You have no power,no wealth, and yet you say such things to me.''

``Yes, it's silly to think I could scare you. After all, you're not aDementor.''
And Harry went on smiling. He'd looked it up, and apparently a bezoar
\emph{would} heal almost any poison if you shoved it into someone'smouth fast enough. Maybe that wouldn't repair radiation damage fromTransfigured polonium, but then again, maybe it would. So Harry hadlooked up the freezing points of various acids, and it turned out thatsulfuric acid would freeze at just ten degrees Celsius, which meantHarry could buy a liter of acid on the Muggle market, freeze it solid,and Transfigure it down to a tiny little unnoticable water-ice chip tobe flipped into someone's mouth and ingested. No bezoar would compensatefor that, once the Transfiguration wore off. Harry had no intention ofsaying it out loud, of course, but now that he'd failed decisively toprevent any deaths during his quest, he had no further intention ofbeing restrained by the law or even the code of Batman.

\emph{Last chance to live, Lucius. Ethically speaking, your life wasbought and paid for the day you committed your first atrocity for theDeath Eaters. You're still human and your life still has intrinsicvalue, but you no longer have the deontological protection of aninnocent. Any good person is licensed to kill you now, if they thinkit'll save net lives in the long run; and I will conclude as much ofyou, if you begin to get in my way. Whoever sent the troll after Grangermust have targeted you too and hit you with some curse that makes formerDeath Eaters melt into a pile of goo. Very sad.}

``Father,'' Draco said in a small voice. ``I think you should considerit, father.''
Lucius Malfoy looked at his son. ``You jest.''

``It's true. I don't think Potter just made up his books, nobody couldhave written all that and there were things in them that I could checkfor myself. And if even half of all that is true, he's right, a hundredthousand Galleons won't mean much. If we give it to him he really willbe friends with House Malfoy again - the way \emph{he} thinks of beingfriends, anyway. And if we don't, he'll be your enemy, whether it's inhis own interests or not, he'll just go after you. Harry Potter reallydoes think like that. It's not about money to him, it's about what hethinks is honor.''
Harry Potter inclined his head, still smiling.

``But let's get one part of it straight,'' Draco said, now staringdirectly at him. There was a fierce light in his eyes. `` \emph{Youwronged me.} And \emph{you owe me.} ''

``Acknowledged,'' Harry said quietly. ``Conditional on the rest of it,of course.''
Lucius Malfoy opened his mouth to say who-knew-what and then closed itagain. ``Mad,'' he said again.
There was a long father-and-son argument during which Harry managed tokeep his mouth shut.
When it seemed that even Draco wouldn't be able to persuade his father,Harry spoke up again, and proposed his intended next steps, if theHouses of Potter and Malfoy could cooperate.
Then came more argument between Lucius and Draco, during which Harryagain stayed silent.
Finally Lucius Malfoy's eyes turned to gaze at Harry. ``And youbelieve,'' Lucius Malfoy said, ``that you can persuade Longbottom andBones to go along with this notion, even if Dumbledore opposes it.''
Harry nodded. ``They'll be suspicious of your involvement, of course.But I'll tell them that it was my plan to start with, and that shouldhelp.''

``I suppose,'' Lucius Malfoy said after a pause, ``that I could have acontract drawn up, absolving you of \emph{almost} all the remainingdebt, if by some chance I do go along with this mad idea. It shall needmore guarantees, of course -''
Harry promptly reached into his robes and drew out a parchment,unfolding it and spreading it across the golden table. ``I've taken theliberty myself, actually,'' Harry said. He'd spent some careful hours inthe Hogwarts library with the law books available. Thankfully, so far asHarry could tell, the laws of magical Britain were charmingly simple byMuggle standards. Writing that the original blood debt and payment wascancelled, the Potters' wealth and all other vault items would bereturned, and the remaining debt annulled, all with no fault to theMalfoys, was only a few more lines than it took to say out loud. ``I hadto promise my keepers not to sign anything you gave me. So I made sureto compose this myself, and sign it before I left.''
Draco emitted a choked laugh.
Lucius read through the contract, smiling humorlessly. ``How charminglystraightforward.''

``I also promised not to touch a quill while I was in Gringotts,'' Harrysaid. He reached into his robes again and drew out a Muggle pen, alongwith a sheet of normal paper. ``Will this wording be all right?'' Harryrapidly scribbled down a legal-sounding statement to the effect thatHouse Potter didn't hold House Malfoy responsible in any way forHermione Granger's murder and didn't believe they had anything to dowith it, then held up the paper in the air for Lord Malfoy's inspection.
Lord Malfoy looked at the paper, rolled his eyes slightly, and said,
``Good enough, I suppose. Though to have the proper meaning, you shoulduse the legal term \emph{indemnify} rather than \emph{exonerate} -''

``Nice try, but no. I know exactly what that word means, Lord Malfoy.''Harry took his parchment and began copying down his original wordingmore carefully.
When Harry was done, Lord Malfoy reached across the golden table andtook the pen, looking at it thoughtfully. ``One of your Muggleartefacts, I suppose? What does this do, son?''

``It writes without needing an inkwell,'' Draco answered.

``I can see that. I suppose some might find it an amusing trinket.''Lucius smoothed the parchment contract over the table, then set his handby the line for signatures, tapping the pen thoughtfully on the startingspot.
Harry wrenched his eyes away, up to Lucius Malfoy's face, forcinghimself to breathe regularly, not quite able to stop his muscles fromtensing.

``Our good friend, Severus Snape,'' said Lucius Malfoy, still tappingthe pen on the line awaiting his signature. ``The Defense Professor,calling himself Quirrell. Now I ask again, who is your third suspect,Harry Potter?''

``I would strongly advise that you sign first, Lord Malfoy, if you'regoing to do so anyway. You will benefit from this information more ifyou do not think I am trying to persuade you of something.''
Another humorless smile. ``I shall take my chances. Speak, if you wishthis to continue.''
Harry hesitated, then said evenly, ``My third suspect is AlbusDumbledore.''
The tapping pen stilled on the parchment. ``A strange allegation,''Lucius drawled. ``Dumbledore lost much face when a Hogwarts student diedwithin his tenure. Do you suppose that I will believe anything of him,only because he is my enemy?''

``He is one suspect among several, Lord Malfoy, and not necessarily themost plausible. But the reason I was able to kill a full-grown mountaintroll was that I had a weapon which Dumbledore gave to me, at the startof the school year. It's not strong evidence, but it's suspicious. Andif you're thinking that murdering one of his students is notDumbledore's style, well, the same thought had occurred to me.''

``It's \emph{not} his style?'' Draco Malfoy said.
Lucius Malfoy shook his head in a measured, careful movement. ``Notquite, my son. Dumbledore is particular in his evils.'' Lord Malfoyleaned back into his chair, and then sat quite still. ``Tell me of thisweapon.''

``I am not yet certain I should go into details about that in yourpresence, Lord Malfoy.'' Harry took a breath. ``Let \emph{me} be clearon this. I am not trying to sell you on the idea that Dumbledore isbehind this, just raising the possibility -''
Then Draco Malfoy spoke. ``The device Dumbledore gave you - was itsomething to kill trolls? I mean, \emph{just} trolls? Can you tell usthat?''
Lucius turned his head to look at his son with some surprise.

``No\ldots{}'' Harry said slowly. ``It wasn't specifically a sword ofanti-troll slaying, or anything like that.''
Draco's eyes were intent. ``Would the device have worked against anassassin?''

\emph{Not if they had shields raised.} ``No.''

``A fight in school?''

\emph{An expanding rock in the throat is inherently lethal.} ``No. Idon't think it was meant for use against humans.'' Draco nodded. ``So just magical creatures. Would it have been a goodweapon against an angry Hippogriff, or something like that?''

``Does the Stunning Hex work on Hippogriffs?'' Harry said slowly.

``I don't know,'' said Draco.

``Yes,'' said Lucius Malfoy.

\emph{Compared to trying to target a Wingardium Leviosa and FiniteIncantatem -} ``Then a Stunning Hex would be a better way of dealingwith a Hippogriff.'' Put that way, it did seem increasingly like aTransfigured rock was an optimal weapon \emph{only} against aflesh-and-blood magical creature with spell-resistant skin.
``But\ldots{} I mean, it might not have \emph{been} intended as a weaponat all, I used it in a strange way, it could have just been a crazy whim
-''

``No,'' Lucius Malfoy said lowly. ``\emph{Not} a whim. Not coincidence.Not Dumbledore.''

``Then it's him,'' Draco said. Slowly Draco's eyes narrowed, and he gavea vicious nod. ``It's been him \emph{since the beginning.} The courtLegilimens \emph{said} that someone had used Legilimency on Granger.Dumbledore \emph{admitted} that it was him. And I bet the wards
\emph{did} go off when Granger cursed me and Dumbledore just
\emph{ignored} them.''

``But -'' Harry said. He looked at Lucius, wondering if it was really tohis advantage to question this idea. ``What would be his \emph{motive?}Are we going to say he's evil and leave it at that?'' Draco Malfoy jumped out of his chair and began pacing around the room,black robes swishing behind the young boy, the goblin guards staring athim in some surprise through their enchanted goggles. ``To figure out astrange plot, look at what happens, then ask who benefits. Except thatDumbledore didn't plan on you trying to save Granger at her trial, hetried to stop you from doing that. What would've happened if Granger \emph{had} gone to Azkaban? House Malfoy and House Potter would've hatedeach other forever. Of all the suspects, the only one who wants \emph{that} is Dumbledore. So it fits. It \emph{all} fits. The one whoreally committed the murder is - Albus Dumbledore!''

``Um,'' Harry said. ``But why give \emph{me} an anti-troll weapon? Isaid it was suspicious, I didn't say that it made any sense.''
Draco nodded thoughtfully. ``Maybe Dumbledore thought you'd stop the troll before it got Granger and then he could blame Father for sending it. A lot of people would be very angry if they thought Father had even \emph{tried} to do something like that, in Hogwarts. Like Father said,Dumbledore must've lost face when people found out that a student hadactually died in Hogwarts, being safe is what Hogwarts is famous for. Sothat part probably wasn't supposed to happen.''
Harry's mind involuntarily flashed back to the horror in Dumbledore'seyes when he'd seen Hermione Granger's body.

\emph{Would I have gotten there in time, if the Weasley twins hadn't hadtheir magic map stolen? Could that have been the plan? And then, thoughDumbledore didn't know it, somebody stole their map, and I was toolate\ldots{} but no, that doesn't make much sense, I found out too late,how could Dumbledore have guessed that I'd use a broomstick\ldots{}well, he did know I had one\ldots{}}
There was no way a plan like that could work.
And it hadn't.
But someone going a little bit senile might \emph{expect} it to work,and a phoenix might not know the difference.

``Or,'' Draco Malfoy continued, still pacing energetically, ``maybeDumbledore had an enchanted troll around, and he expected you to defeatit some other time, for some other plot, and then he used the troll onGranger instead. I can't imagine Dumbledore had this \emph{all} plannedsince the first week of lessons -''

``I can imagine,'' Lucius Malfoy said in low tones. ``I have seen such,from Dumbledore.''
Draco nodded decisively. ``Then I was never \emph{supposed} to die inthe first plot. Dumbledore knew Professor Quirrell was checking on me,or Dumbledore planned to have someone else find me in time - I couldn'thave testified against Granger if I was dead, and he'd have lost face ifI'd died. But my leaving Hogwarts and not being around to lead Slytherinwould be just right for him. And then the next time Harry was supposedto stop the troll before it got Granger and everyone was supposed toblame you, Father, only that time it didn't go the way Dumbledoreplanned.''
Lucius Malfoy lifted his grey eyes, from where he'd been gazing withopen surprise at his son. ``If this is true - but I wonder if HarryPotter is only playing at being reluctant to believe it.''

``Maybe,'' Draco said. ``But I'm pretty sure he isn't.''

``Then, if it is true\ldots{}'' Lucius Malfoy's voice trailed off. Aslow fury was lighting in his eyes.

``What \emph{would} we do, exactly?'' Harry said.

``That, too, is clear to me,'' Draco said. He whirled on them and raiseda finger high in the air. ``We shall find the proof to convictDumbledore of this crime, and bring him to justice!''
Harry Potter and Lucius Malfoy looked at each other.
Neither of them quite knew what to say.

``My son,'' Lucius Malfoy said after a time, ``truly, you have done verywell this day.''

``Thank you, Father!''

``However, this is not a play, we are not Aurors, and we do not put ourtrust in trials.''
Some of the light went out of Draco's eyes. ``Oh.''

``I, ah, do have a sentimental fondness for trials,'' Harry interjected.
\emph{I cannot believe I am having this conversation.} He needed to gohome and take a sheet of paper and a pencil and try to figure outwhether Draco's reasoning \emph{actually} made sense. ``And evidence.''
Lucius Malfoy turned his gaze to Harry Potter then, and his eyessimmered in pure grey fury.

``If you have deceived me,'' Lucius Malfoy said in tones of low anger,
``if all this is a lie, then I will not forgive. But if this is notdeception\ldots{} Bring me the proof to convict Dumbledore of thismurder before the Wizengamot, or evidence enough to have him cast down,and there is nothing that House Malfoy will not do for you, HarryPotter. Nothing.''
Harry took a deep breath. He needed to sort all this out and figure outthe actual probabilities, but he didn't have \emph{time} . ``If it
\emph{is} Dumbledore, then removing him from the gameboard leaves a hugehole in Britain's power structure.''

``So it does,'' Lucius Malfoy said with a grim smile. ``Did you haveambitions of filling it yourself, Harry Potter?''

``Some of your opposition might not like that. They could fight.''

``They will lose,'' Lucius Malfoy said, now with a face hard like iron.

``So this is what I'd want House Malfoy to do for me, Lord Malfoy, ifDumbledore gets removed because of me. When the opposition is mostfrightened - that's when they'll be offered a last-minute arrangement toavoid a civil war. Some of your allies might not prefer it, but there'llbe a lot of neutrals who'll be glad to see stability. The bargain willbe that instead of you taking over right away, Draco Malfoy will takepower when he comes of age.''

" \emph{What?} " Draco said.

``Draco has testified under Veritaserum that he tried to help HermioneGranger. I bet there'd be a lot of people in the opposition who'd take achance on him rather than fight. I'm not sure how exactly you'd enforceit - Unbreakable Vows or Gringotts contracts or what - but there'll besome sort of enforceable compact about power going to Draco after hegraduates Hogwarts. I'll throw any support the Boy-Who-Lived has behindthat bargain. Try to persuade Longbottom and Bones and so on. Our firstplan paves the way for that later, if you're careful to act honorablewhen you deal with Longbottom and Bones this time around.''

``Father, I \emph{swear} I didn't -''
Lucius's face twisted into a grim smile. ``I know you didn't, son.Well.'' The white-haired man stared across the mighty golden table atHarry Potter. ``Those terms are acceptable to me. But fail in any partof our agreement, whether our first bargain, or the second, and thereshall be consequences for you, Harry Potter. Clever words will not haltthat.''
And Lucius Malfoy signed the parchment.

\begin{center}\rule{3in}{0.4pt}\end{center}
Mad-Eye Moody had been staring at the bronze door of the Gringottsmeeting room for what seemed like hours, insofar as a man could stare atany one thing when his gaze always saw in all directions.
The trouble with trying to be suspicious of a man like Lucius Malfoy,Moody thought, was that you could spend an entire day thinking ofeverything he might be up to, and still not have finished.
The door cracked open and Harry Potter trudged out, small beads of sweatstill on his forehead.

``Did you sign anything?'' Mad-Eye demanded upon the instant.
Harry Potter looked at him silently, then reached into his robes anddrew out a folded parchment. ``The goblins are already executing this,''said Harry Potter. ``They made three copies before I left.''

``MERLIN DAMN IT SON -'' Moody paused as his Eye caught sight of thesecond half of the document as Harry Potter slowly, as thoughreluctantly, began to unfold the top upward. A glance sufficed to takein the paragraphs drawn in careful handwriting, Lucius Malfoy's elegantsignature below Harry Potter's. And then Moody exploded, even as the tophalf of the document also began to enter his Sight. ``You
\emph{exonerate House Malfoy} of \emph{any involvement in HermioneGranger's death?} Do you have any idea what you've done, you littlefool? Why in Merlin's name would you do something like WHAT -''