\chapter{Precautionary Measures, Pt 1}

\emph{May 13th, 1992.}
Argus Filch's face appeared twisted in the light of the oil lamp heheld, shadows dancing over his face. Behind them the doors of Hogwartsquickly receded, and the dark grounds moved closer. The track they nowwalked was muddy and indistinct.
The trees, branches formerly bare with winter, were not yet fully cladwith spring; their branches stretched up toward the sky like leanfingers, skeletons visible amid the thin foliage. The moon was bright,but clouds scudding across it often threw them into darkness, lit onlyby the dim flames of Filch's lamp.
Draco kept a firm grip on his wand.

``Where are you taking us?'' said Tracey Davis. She'd been caught alongwith Draco by Filch, on their way to an attempted meeting of the SilverySlytherins after curfew hours, and likewise given a detention.

``You just follow me,'' said Argus Filch.
Draco was feeling rather annoyed with the whole affair. The SilverySlytherins ought to be recognized school business. There was no reasonwhy a secret conspiracy shouldn't have permission to meet after curfew,if it was for the greater good of Hogwarts. If this happened one moretime he'd talk to Daphne Greengrass and Daphne would talk to her fatherand then Filch would learn the wisdom of looking the other way whereMalfoys were concerned.
The lights of the Hogwarts castle had diminished in the distance whenFilch spoke again. ``I bet you'll think twice about breaking a schoolrule again, won't you, eh?'' Filch turned his head, away from the lamp,so that he could leer at the four students following him. ``Ohyes\ldots{} hard work and pain are the best teachers if you askme\ldots{} It's just a pity they let the old punishments die out\ldots{}hang you by your wrists from the ceiling for a few days, I've got thechains still in my office, keep 'em well oiled in case they're everneeded\ldots{}''

``Hey!'' Tracey said, a touch of indignation entering her voice. ``I'mtoo young to hear about that - that sort of - you know! Especially ifthe chains are well-oiled!''
Draco wasn't paying attention. Filch simply wasn't in Amycus Carrow'sleague.
Behind them, one of the two older Slytherins following them snickered,though she didn't say anything. Beside her was the other, a tall boywith an Slavic cast to his face, and who still spoke with an accent.They'd been caught for some unrelated offense, having to do with thetype of thing Tracey went on about, and looked to be in their third orfourth year. ``Pfeh,'' said the taller boy. ``In Durmstrang they hangyou upside-down by your toes. By one toe, if you are insolent. Hogwartswas soft even in the old days.''
Argus Filch was silent for around half a minute, as though trying tothink of a proper rejoinder, and then gave a chuckle. ``We'll see whatyou say about that\ldots{} when you learn what you'll be doing tonight!Ha!''

``I \emph{said,} I'm too young for that sort of thing!'' said TraceyDavis. ``It has to wait until I'm older!''
Ahead of them was a cottage with lighted windows, though the proportionsseemed wrong.
Filch whistled, a high sharp sound, and a dog began barking.
From the cottage stepped forth a figure, making the trees seem too shortaround it. The figure was followed by a dog that seemed like a puppy bycomparison, until you looked at it apart from the taller silhouette andrealized the dog was huge, more like a wolf.
Draco's eyes narrowed, before he caught himself. As a Silvery Slytherinhe wasn't supposed to be Prejudiced against any sentient being,especially not where other people might see him.

``What's this?'' said the figure, in the loud gruff voice of thehalf-giant. His umbrella lit up with a white glow, brighter than Filch'sdim lamp. In his other hand he held a crossbow; a quiver of short boltswas strapped to his upper arm.

``Students serving detention,'' Filch said, loudly. ``They're to helpyou search the Forest for\ldots{} whatever's been eating 'em.''

``The \emph{Forest?}'' gasped Tracey. ``We can't go in there at night!''

``That's right,'' said Filch, turning from Hagrid to glare at them.
``It's into the Forest you're going, and I'm much mistaken if you'll allcome out in one piece.''

``But -'' said Tracey. ``There's werewolves, I've heard, \emph{and}vampires, and everyone knows what happens when there's a girl and awerewolf and a vampire all at the same time!''
The huge half-giant was frowning. ``Argus, I `ad in mind you an' maybe afew seventh-years. 'Ere's not much point in bringing along help if I'mto watch over 'em the whole time.''
Argus's face lit with cruel satisfaction. ``That's their lookout, isn'tit? Should've thought of them werewolves before they got in trouble,shouldn't they? Send them out alone. I shouldn't be too friendly tothem, Hagrid. They're here to be punished, after all.''
The half-giant gave a massive sigh (it sounded like a normal man havingall the air driven out of his lungs by a Bludgeoning Hex). ``Yeh've doneyer bit. I'll take over from here.''

``I'll be back at dawn,'' said Filch, ``for what's left of them,'' headded nastily, and he turned and started back toward the castle, hislamp bobbing away in the darkness.

``Right then,'' said Hagrid, ``now, listen carefully, `cause it'sdangerous what we're gonna do tonight an' I don' want no one takin'risks. Follow me over here a moment.''
He led them to the very edge of the Forest. Holding his lamp up high hepointed down a narrow, winding earth track that disappeared into thethick black trees. A light breeze blew over Draco's head as he lookedinto the Forest.

``There's summat in there that's bin eatin' unicorns,'' the huge mansaid.
Draco nodded; he distantly remembered hearing something along thoselines a couple of weeks ago, toward the end of April.

``Did you call us to track down a trail of silvery blood to a woundedunicorn?'' Tracey said excitedly.

``No,'' said Draco, though he managed to stop the reflexive sneer.
``Filch gave us the detention note at lunch today, at noon. Mr.~Hagridwouldn't wait that long to find a wounded unicorn, and if we werelooking for something like that, we'd look in the day when it's bright.So,'' Draco held up a finger, like he'd seen Inspector León do in plays,
``I infer that we're looking for something that only comes out atnight.''

``Aye,'' said the half-giant, sounding thoughtful. ``Yer not what Iexpected, Draco Malfoy. Not what I expected at all. An' you'd be TraceyDavis, then. I've heard of yeh. One of poor Miss Granger's lot.'' RubeusHagrid looked over at the two older Slytherins, peering at them in thelight of his glowing umbrella. ``An' who'd yeh be, again? Don't rememberseeing much of yeh, boy.''

``Cornelia Walt,'' said the witch, ``and this is Yuri Yuliy,''indicating the Slavic-looking boy who'd spoken of Durmstrang. ``Hisfamily is visiting from the Ukrainian lands, so he's in Hogwarts justfor the year.'' The older boy nodded, a faintly contemptuous cast on hisface.

``This is Fang,'' Hagrid said, indicating the dog.
The five of them set off into the woods.

``What could be killing unicorns?'' Draco said after they'd walked for afew minutes. Draco knew a bit about Dark creatures, but he couldn'tremember anything that was said to prey on unicorns. ``What sort ofcreature does that, does anyone know?''

``Werewolves!'' said Tracey.

``Miss Davis?'' Draco said, and when she looked at him, he silentlypointed a finger up at the moon. It was waxing gibbous, but not yetfull.

``Oh, right,'' said Tracey.

``No weres in the Forest,'' said Hagrid. ``They're plain wizards most o'the time, 'member. Couldn't be wolves either, they're not near fastenough ter catch a unicorn. Powerful magical creatures, unicorns are, Inever knew one ter be hurt before.''
Draco listened to this, thinking about the puzzle almost despitehimself. ``Then what \emph{is} fast enough to catch a unicorn?''

``Wouldn't 'ave been a matter of speed,'' Hagrid said, giving Draco anindecipherable glance. ``Ere's no end ter the ways that creatures hunt.Poison, darkness, traps. Imps as can't be seen or heard or remembered,even while they're eatin' yer face. Always summat new an' wonderful tolearn.''
A cloud passed over the moon, casting the forest into shadow lit only bythe glow of Hagrid's umbrella.

``Meself,'' Hagrid continued, ``I think we might `ave a Parisian hydraon our 'ands. They're no threat to a wizard, yeh've just got to keepholdin' `em off long enough, and there's no way yeh can lose. I meanliterally no way yeh can lose so long's yeh keep fightin'. Trouble is,against a Parisian hydra, most creatures give up long before. Takes awhile to cut down all the heads, yeh see.''

``Bah,'' said the foreign boy. ``In Durmstrang we learn to fightBuchholz hydra. Unimaginably more tedious to fight! I mean literally,cannot imagine. First-years not believe us when we tell them winning ispossible! Instructor must give second order, iterate until theycomprehend.''
They walked for nearly half an hour, deeper and deeper into the Forest,until the path became almost impossible to follow because the trees wereso thick.
Then Draco saw it, thick splashes on the roots of trees, gleaming abrighter color beneath the moonlight. ``Is that -''

``Unicorn's blood,'' Hagrid said. The huge man's voice was sad.
In a clearing ahead, visible through the tangled branches of a greatoak, they saw the fallen creature, splayed beautiful and sad upon theground, the dirt around her shining moon-silver with pooled blood. Theunicorn was not white, but pale blue, or appearing so beneath the moonand night sky. Her slender legs stuck out at odd angles, obviouslybroken, and her mane spread across the dark leaves, green-black but witha sheen like pearls. On her flank was a small white shape like astarburst, a center surrounded by eight straight rays. Half her side hadbeen ripped away, the edges ragged like the marks of teeth, bones andinner organs exposed.
A strange choking sensation rose in Draco's throat.

``That's 'er,'' Hagrid said, his sad whisper as loud as a normal man'svoice. ``Just where I found `er this mornin', dead as a dead doorknob.She is - was - the first unicorn I e'er met in these woods. I called 'erAlicorn, not that it matters ter 'er any more, I s'pose.''

``You named a unicorn Alicorn,'' said the older girl. Her voice was abit dry.

``But she doesn't have wings,'' Tracey said.

``An alicorn's a unicorn's horn,'' Hagrid said, now louder. ``Don't knowwhere yeh all started thinking it meant a unicorn with wings, 'ere's nosuch thing I ever heard. It's just like naming a dog Fang,'' indicatingthe huge wolf-like dog that barely came to his knees. ``What'd you havecalled 'er? Hannah, or some such? I gave 'er a name as would've meantsummat ter \emph{'er.} Common courtesy, I call it.''
Nobody said anything to this, and after a further moment, the huge mangave a sharp nod. ``We'll start our search from `ere, the last place itstruck. We're gonna split inter two parties an' follow the trail indiff'rent directions. Yeh two, Walt and Yuliy - yeh'll go that way, andtake Fang. There's nothin' that lives in the Forest that'll hurt yeh ifyer with Fang. Send up green sparks if yeh find summat interestin', an'send up red sparks if anyone gets in trouble. Davis, Malfoy, with me.''
The Forest was black and silent. Rubeus Hagrid had dimmed the light ofhis umbrella after they'd set out, so that Draco and Tracey had to steerthemselves by the light of the moon, not without occasional trips andfalls. They walked past a mossy tree-stump, the sound of running waterspeaking of a stream somewhere close by. Now and then a ray of moonlightthrough the branches above lit a spot of silver blue blood on the fallenleaves; they were following the trail of blood, toward where thecreature must have first struck the unicorn.

``There's rumors about yeh,'' Hagrid said in a low voice after they'dwalked for a while.

``Well, they're all true,'' Tracey said. *``All* of them.''

``Not yeh,'' Hagrid said. ``Did yeh really testify under Veritaserumthat yeh tried to help Miss Granger, three times it was?''
Draco weighed his words for a while, and finally said, ``Yes.'' Itwouldn't have done to appear too eager to claim credit.
The huge man shook his head, his great feet still stomping silentlythrough the woods. ``I'm surprised, teh be honest. And yeh too, Davis,tryin' to put the halls in order. Are yeh sure the Sorting Hat put yehin the right place? There's not a single witch or wizard who went badwho wasn't in Slytherin, so it's always been said.''

``That's not true,'' Tracey said. ``What about Xiaonan Tong the BlackRaven, Spencer of the Hill, and Mister Kayvon?''

``Who?'' said Hagrid.

``Just some of the best Dark Wizards from the last two centuries,''Tracey said. ``They're probably \emph{the} best from Hogwarts whoweren't from Slytherin.'' Her voice fell, lost its enthusiasm. ``MissGranger always told me I should read up on anything I -''

\emph{``Anyway,''} Draco said quickly, ``that's not really relevant,Mr.~Hagrid. Even if -'' Draco worked it around in his head, trying totranslate the difference between \emph{probability of Slytherin givenDark} and \emph{probability of Dark given Slytherin} into nonscientificlanguage. ``Even if most Dark Wizards are from Slytherin, very fewSlytherins are Dark Wizards. There aren't all that many Dark Wizards, sonot all Slytherins can be one.'' Or as Father had said, while any Malfoyshould certainly know much of the secret lore, the more\ldots{}
\emph{costly} rituals were better left to useful fools like AmycusCarrow.

``So yeh're saying,'' Hagrid said, ``that most Dark Wizards areSlytherins\ldots{} but\ldots{}''

``But most Slytherins are not Dark Wizards,'' Draco said. He had a wearyfeeling they'd be at this a while, but like fighting a hydra, theimportant thing was to not give up.

``I never thought of it that way,'' the huge man said, soundingawestruck. ``But, well, if yeh're not all a house of snakes, then why -
\emph{get behind that tree!}''
Hagrid seized Draco and Tracey and hoisted them off the path behind atowering oak. He pulled out an arrow and fitted it into his crossbow,raising it, ready to fire. The three of them listened. Something wasslithering over dead leaves nearby: it sounded like a cloak trailingalong the ground. Hagrid was squinting up the dark path, but after a fewseconds, the sound faded away.

``I knew it,'' Hagrid murmured. ``There's summat in here that shouldn'be.''
They went after where the rustling sound had come from, with Hagrid inthe lead and Tracey and Draco both gripping their wands at the ready,but they found nothing, despite searching in a widening circle withtheir ears straining for the faintest sound.
They walked on through the dense, dark trees. Draco kept looking overhis shoulder, a feeling nagging at him that they were being watched.They had just passed a bend in the path when Tracey yelled and pointed.
In the distance, a shower of red sparks lit the air.

``You two wait here!'' Hagrid shouted. ``Stay where yeh are, I'll comeback for yeh!''
Before Draco could say a word, Hagrid spun and crashed away through theundergrowth.
Draco and Tracey stood looking at each other, until they heard nothingbut the rustling of leaves around them. Tracey looked scared, but tryingto hide it. Draco was feeling more annoyed than anything else. One hadthe distinct impression that Rubeus Hagrid, when he had formed his plansfor tonight, had not spent even five seconds visualizing theconsequences if something actually went wrong.

``Now what?'' said Tracey, her voice a little high.

``We wait for Mr.~Hagrid to come back.''
The minutes dragged by. Draco's ears seemed sharper than usual, pickingup every sigh of the wind, every cracking twig. Tracey kept looking upat the moon, as though to reassure herself that it wasn't full yet.

``I'm -'' Tracey whispered. ``I'm getting a little nervous,Mr.~Malfoy.''
Draco thought about it a bit. To be honest, there \emph{was}something\ldots{} well, it wasn't that he was a coward, or even that hewas scared. But there had been a murder at Hogwarts and if he'd beenwatching himself in a play, having just been abandoned in the ForbiddenForest by a half-giant, he would currently feel like yelling at the boyon stage that he should\ldots{}
Draco reached into his robes, and took out a mirror. Tapping the surfaceshowed a man in red robes, who frowned almost immediately.

``Auror Captain Eneasz Brodski,'' the man said clearly, causing Traceyto start with the loudness in the quiet forest. ``What is it, DracoMalfoy?''

``Put me on ten-minute check-in,'' Draco said. He'd decided not tocomplain directly about his detention. He did \emph{not} want to looklike a spoiled brat. ``If I don't respond, come get me. I'm in theForbidden Forest.''
Inside the mirror, the Auror's brows rose. ``What are you doing in theForbidden Forest, Mr.~Malfoy?''

``Looking for the unicorn-eater with Mr.~Hagrid,'' Draco said, andtapped the mirror off, putting it back in his robes before the Aurorcould ask anything about detentions or say anything about serving it outwithout complaining.
Tracey's head turned toward him, though it was a little too dim to readher expression. ``Um, thanks,'' she whispered.
The few leaves which had emerged on their branches rustled as another,colder breeze blew through the forest.
Tracey's voice was a little louder when she spoke again. ``You didn'thave to -'' she said, now sounding a little shy.

``Don't mention it, Miss Davis.''
The dark silhouette of Tracey put her hand to her cheek, as though toconceal a blush that wasn't visible anyway. ``I mean, not for \emph{me}
-''

``No, really,'' Draco said. ``Don't mention it. At all.'' He would havethreatened to take out the mirror and order Captain Brodski not torescue \emph{her,} but he was afraid she would consider that flirting.
Tracey's silhouetted head turned from him, looked away. Finally shesaid, in a smaller voice, ``It's too soon, isn't it -''
A high scream echoed through the woods, a not-quite-human sound, thescream of something like a horse; and Tracey shrieked and ran.

*``No, you nimrod!*'' yelled Draco, plunging after her. The sound hadbeen so eerie that Draco wasn't absolutely certain where it came from -but he thought that Tracey Davis might, in fact, be running straighttoward the source of that eerie scream.
Brambles whipped at Draco's eyes, he had to keep one hand in front ofhis face to shield them, trying not to lose track of Tracey because itseemed obvious that, if this was a play, and they got separated,
\emph{one} of them was going to die. Draco thought of the mirror securedwithin his robes but he somehow knew that if he tried to take it outone-handed while running, the mirror would inevitably fall and be lost -
Ahead of them, Tracey had stopped, and Draco felt relieved for aninstant, before he saw.
Another unicorn lay on the ground, surrounded by a slowly widening poolof silver blood, the edge of the blood creeping across the ground likespilled mercury. Her coat was purple, like the color of the night sky,her horn exactly the same twilight color as her skin, her visible flankmarked by a pink star-blotch surrounded by white patches. The sight toreat Draco's heart, even more than the other unicorn because this one'seyes were staring glassily right at him, and because there was a -

\begin{itemize}
\item
  blurring, twisting form -
\item
  feeding on an open wound on the unicorn's side, like it was drinking
  from it -
\item
  Draco couldn't understand, somehow couldn't recognize what he was
  seeing -
\item
  \emph{it was looking at them.}
\end{itemize}
The blurring, seething, unrecognizable darkness seemed to turn to regardthem. A hiss came from it, like the hiss of the deadliest snake whichever had existed, something more dangerous by far than any Blue Krait.
Then it bent back over the wound in the unicorn, and continued to drink.
The mirror was in Draco's hand, and it remained lifeless as his fingermechanically tapped at the surface, over and over.
Tracey was holding her wand now, saying things like ``Prismatis'' and
``Stupefy'' but nothing was happening.
Then the seething outline rose up, like a man rising to his feet onlynot so; and it seemed to scuttle forward, moving with a strangehalf-jump across the dying unicorn's legs, approaching the two of them.
Tracey tugged at his sleeve and then turned to run, run from somethingthat could hunt down unicorns. Before she could take three steps therecame another terrible hiss, burning his ears, and Tracey fell to theground and did not move.
Somewhere in the back of his mind, Draco knew that he was about to die.Even if the Auror checked his mirror this very instant, there was no wayanyone could get here fast enough. There was no \emph{time.}
Running hadn't worked.
Magic hadn't worked.
The seething outline came closer, while Draco tried, in his lastmoments, to solve the riddle.
Then a blazing silver ball of light plunged out of the night sky andhung there, illuminating the forest as bright as daylight, and theseething outline leapt backwards, as though in horror of the light.
Four broomsticks plunged out of the sky, three Aurors with brightmulticolored shields and Harry Potter holding his wand aloft, seatedbehind Professor McGonagall within a larger shield.

``Get out of here!'' roared Professor McGonagall -

\emph{- an instant before the seething thing gave forth another terriblehiss, and all the shielding spells winked out. The three Aurors andProfessor McGonagall fell off their broomsticks and dropped heavily tothe forest floor, lying motionless.}

\emph{Draco couldn't breathe, the most intense fear he'd ever felt inhis life gripping all through his chest, sending tendrils around hisheart.}

\emph{Harry Potter, who had remained untouched, silently guided hisbroomstick toward the ground -}

\emph{- and then leapt off to stand between Draco and the seethingoutline, interposing himself like a living shield.}

\emph{``Run!'' said Harry Potter, turning his head half-back to look atDraco. The silver moonlight gleamed on his face. ``Run, Draco! I'll holdit off!''}

\emph{``You can't fight that thing alone!'' Draco cried aloud. A nauseawas in his stomach, a churning sensation that, looking back in memory,seemed both like and unlike a sense of guilt, as though it had thesensations but not quite all of the emotion.}

\emph{``I must,'' Harry Potter said grimly. ``Go!''}

\emph{``Harry, I - I'm sorry, for everything - I'' Though later, lookingback, Draco couldn't quite remember what he'd meant to apologize for,maybe it'd been that he was planning to overthow Harry's conspiracy, allthat time ago.}

\emph{The seething figure, now seeming blacker and more terrible, roseup into the air, hovering off the ground.}

\emph{``GO!'' shouted Harry.}

\emph{Draco turned and fled headlong into the woods,with the brancheswhipping at his face. Behind him, Draco heard another terrible hiss, andHarry's voice rising, crying something that Draco couldn't make out fromthe distance; Draco turned his head for only an instant to look back,and in that moment ran into something, hitting his head HARD, andblacked out.}

\begin{center}\rule{3in}{0.4pt}\end{center}
Harry held a tight grip on his wand, a Prismatic Sphere glowing aroundhim. He stared levelly at the seething, blurring form in front of him,and said, ``What on Earth are you doing?''
The seething blurs resolved, reformed, relaxed back into a hooded form.Whatever concealment had been at work - a device rather than a Charm,Harry guessed, since the magic had been able to affect him - hadprevented his mind from recognizing the shape or even that the shape washuman. But it hadn't prevented Harry from recognizing the sharp sense ofdoom.
Professor Quirrell stood straight with silver blood all down the frontof his enshrouding black cloak, and gave a sigh, looking at the fallenforms of three Aurors, Tracey Davis, Draco Malfoy, and ProfessorMcGonagall. ``I had honestly thought,'' Professor Quirrell murmured,
``that I jammed that mirror without alarm. What were two first-yearSlytherins doing alone in the Forbidden Forest? Mr.~Malfoy has moresense than this\ldots{} What a fiasco.''
Harry didn't answer. The sense of doom was as strong as Harry could everremember feeling it, a feeling of power in the air so great that it wasalmost tangible. Some part of him was still viscerally shocked at howfast the shields surrounding the Aurors had been torn apart. He almosthadn't been able to \emph{see} the successive lashes of color which hadtorn away the shields like tissue paper. It made the duel ProfessorQuirrell had fought against the Auror in Azkaban look like a mockery, achild's game - though Professor Quirrell had claimed, then, that if he'dfought for real the Auror would have been dead in seconds; and Harryknew now that this was also true.
Just how high did the power ladder go?

``I take it,'' Harry said, managing to keep his voice steady, ``thatyour eating unicorns has something to do with why you'll get fired fromthe Defense Professor position. I don't suppose you'd care to explain inconsiderable detail?''
Professor Quirrell looked at him. The almost tangible sense of power inthe air seemed to diminish, drawing back into the Defense Professor. ``Ishall indeed explain myself,'' the Defense Professor said. ``I need tocast a few Memory Charms first, and then we may go off and discuss it,for it would not be wise for me to stay. You will return to this timelater, as I know.''
Harry willed himself to be able to see through the Cloak he hadmastered; and knew that another Harry stood beside him, hidden by hisown Deathly Hallow. Harry then told his Cloak to hide himself fromhimself once more, and it did; being able to perceive your future selfmeant having to match the memory later.
Harry's own voice said, then, sounding strange in present-Harry's ears,
``He has a surprisingly good explanation.''
Present-Harry remembered the words as best he could. Nothing more wassaid between them.
Professor Quirrell walked to Draco's form, and chanted the spell of theFalse Memory Charm. The Defense Professor stood there for perhaps aminute, seemingly lost to the world.
Harry had been studying Memory Charms, these last couple of weeks -though he couldn't have helped cast the spells, unless he was willing toexhaust himself almost completely, and for some reason they wanted anAuror to lose every single life memory involving the color blue. ButHarry had some idea, now, of the concentration which the far moredifficult False Memory Charm entailed. You had to try to live the otherperson's entire life inside your own head, at least if you wanted tocreate the False Memories with less than a sixteen-to-one slowdown asyou separately crafted sixteen major tracks of memory. It might havebeen quiet, there might have been no outward sign; but Harry knewsomething of the difficulties now, and he knew to be impressed.
Professor Quirrell finished, and moved on to Tracey Davis, then thethree Aurors, and finally Professor McGonagall. Harry waited, butfuture-Harry made no protest. It was possible that even ProfessorMcGonagall, if she'd been awake, wouldn't have protested. It was not yetthe Ides of May, and apparently there would be a surprisingly goodexplanation.
With a gesture, Draco's stunned body was lifted, and sent a shortdistance into the woods, before being carefully deposited on the ground.Then a final gesture from Professor Quirrell ripped a huge chunk out ofthe unicorn's side, leaving behind ragged edges; the raw meat hovered inthe air, then wavered in Vanishment and was gone.

``Done,'' Professor Quirrell said. ``I must depart this place now,Mr.~Potter. Come with me, and remain here.''
Professor Quirrell strode away, and Harry followed and remained behind.
They walked through the woods in silence for a time, before Harry heardfaint voices in the distance. The next set of Aurors, presumably, afterthe first set had fallen out of contact. What his future self wassaying, Harry didn't know.

``They won't detect us, nor hear our speech,'' said Professor Quirrell.The sense of power and doom around the Defense Professor was stillstrong. The man seated himself on a tree stump, one where the light ofthe almost-full moon fell full on him. ``I should first say that whenyou speak to the Aurors, in the future, you should tell them that youfrightened away the seething dark, the same as you did that Dementor. Itis what Mr.~Malfoy will remember seeing.'' Professor Quirrell gave asmall sigh. ``It may cause some alarm, if they conclude that some horrorkin to Dementors, and strong enough to break the Aurors' shields, isloose in the Forbidden Forest. But I could not think of what else to do.If the forest is better-guarded after this - but with any luck I havealready consumed what I need. Would you mind telling me how you arrivedso quickly? How did you know Mr.~Malfoy was in trouble?''
After Captain Brodski had learned that Draco Malfoy was in the ForbiddenForest, seemingly in the company of Rubeus Hagrid, Brodski had beguninquiring to find out who had authorized this, and had still been unableto find out when Draco Malfoy had missed check-in. Despite Harry'sprotests, the Auror Captain, who was authorized to know aboutTime-Turners, had refused to allow deployment to before the time of themissed check-in; there were standard procedures involving Time. ButBrodski had given Harry written orders allowing him to go back anddeploy an Auror trio to arrive one second after the missed check-intime. There had been a Patronus Charm to locate Draco, which Harry hadsuccessfully willed to take the form of a ball of pure silver light, andthe flight of Aurors had arrived on time to the second.

``I'm afraid I couldn't say,'' Harry replied evenly. Professor Quirrellwas still a major suspect, and it was good for him not to know thedetails. ``Now why are you eating unicorns?''

``Ah,'' Professor Quirrell said. ``As to that\ldots{}'' The manhesitated. ``I was drinking the blood of unicorns, not eating them. Themissing flesh, the ragged marks upon the body - those were to obscurethe case, to make it seem like some other predator. The use of unicorn'sblood is too well-known.''

``I don't know it,'' Harry said.

``I know you do not,'' the Defense Professor said sharply. ``Or youwould not be pestering me about it. The power of unicorn's blood is topreserve your life for a time, even if you are on the very verge ofdeath.''
There was a stretch of time when Harry's brain claimed to be refusing toprocess the words, which was of course a lie, because you couldn't knowthe meaning you weren't allowed to process, without having alreadyprocessed it.
A strange sense of blankness overtook Harry, an absence of reaction,maybe this was what other people felt like when someone went off-script,and they couldn't say or think of anything to do.
Of course Professor Quirrell was dying, not just occasionally ill.
Professor Quirrell had known he was dying. He'd volunteered to take theDefense Professor position at Hogwarts, after all.
Of course he'd been getting worse the whole school year. Of courseillnesses which kept getting worse had a predictable destination attheir end.
Harry's brain had surely known already, somewhere in the safe back ofhis mind where he could refuse to process things he'd already processed.
Of course that was why Professor Quirrell wouldn't be able to teachBattle Magic next year. Professor McGonagall wouldn't even have to firehim. He would just be -

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  dead.
\end{itemize}

``No,'' Harry said, his voice a little shaky. ``There has to be a way
-''

``I am not stupid nor particularly eager to die. I have already looked.I had to go this far simply to last out my lesson plans, having lesstime than I had thought, and -'' The head of the dark moonlit figureturned away. ``I think I do not want to hear about it, Mr.~Potter.''
Harry's breath hitched. Too many emotions were bubbling up in him atonce. After denial came anger, according to a ritual someone had justmade up. And yet it seemed surprisingly appropriate.

``And why -'' Harry's breath hitched again. ``Why isn't unicorn's bloodstandard in healer's kits, then? To keep someone alive, even if they'reon the very verge of dying from their legs being eaten?''

``Because there are permanent side effects,'' Professor Quirrell saidquietly.

``Side effects? \emph{Side effects?} What kind of side effect ismedically worse than \emph{DEATH?}'' Harry's voice rose on the last worduntil he was shouting.

``Not everyone thinks the same way we do, Mr.~Potter. Though, to befair, the blood must come from a live unicorn and the unicorn must diein the drinking. Would I be here otherwise?''
Harry turned, stared at the surrounding trees. ``Have a herd of unicornsat St.~Mungos. Floo the patients there, or use portkeys.''

``Yes, that would work.''
Harry's face tightened, the only outward sign behind his trembling handsof everything that was welling up inside him. He needed to scream,needed some outlet, needed \emph{something} he couldn't name and finallyHarry leveled his wand at a tree and shouted *``Diffindo!*''
There was a sharp tearing sound, and a cut appeared across the wood.

\emph{``Diffindo!''}
Another cut. Harry had learned the Charm only ten days previously, afterhe'd started getting serious about self-defense. It was theoretically asecond-year Charm, but the anger pouring through him seemed to know nobounds, he knew enough now not to exhaust himself and he still had poweryet.

*``Diffindo!*'' Harry had aimed at a branch this time, and it plummetedto the ground with a sound of twigs and leaves.
There didn't seem to be any tears inside him, only pressure with nooutlet.

``I shall leave you to it,'' Professor Quirrell said quietly. TheDefense Professor rose from his tree stump, the unicorn's blood stillmoonlit on the black cloak he wore, and drew his hood back over hishead.